---
title: "Dynamic calculations of fire Disturbance Matrices for GCBM including fire severity"
author: "Thompson and Whitman"
format: pdf
editor: visual
---

## Global Variables

Certain variables, like the fractionation of CO2:CH4:CO, are constant throughout ecozones, but vary by flaming vs smouldering. They are defined in a global variables table:

```{r defineVars, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(kableExtra)
library(tinytex)
library(formatR)
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE)

#populate the values first:
global.vars <- list(0.9, 0.01, 0.09, 0.77, 0.03, 0.21)
#then label names
names(global.vars) <- array(c("FlamingCO2","FlamingCH4","FlamingCO","SmoulderingCO2","SmoulderingCH4","SmoulderingCO"))

#DID NOT RUN:
#global.vars$FlamingCO2 #returns desired value as double

#can add/subtract ecozones here as needed.  Note that Mixedwood Plains not included here (but could/should be)
ecozones.list <- list("AM","TP","TSW","BSW","BP","P","TC","BC","PM","MC","HP","TSE","BSE")

```

## Duff Consumption

To be expanded later, but duff consumption can be calculated annually using the median hotspot Drought Code and de Groot's FFFC equations, as applied to median FFFL values. Could also be done per fire using fire-specific DC and mapped FFFC values as well. Need to compute this above for use below.

```{r computeDuffConsump, echo=FALSE,message=FALSE, warning=FALSE}
#load an array of median DC values by ecozone (provided here hardcoded from Quinn Barber's dataframes of all Canadian hotspots from CWFIS 2002-2022), using the exact same order of ecozones above:
Median.DC <- c(270,369,297,239,242,242,254,250,268,452,204,98,123)

# then the median forest floor load, minus an average litter value (provided here hardcoded from 10.1139/x2012-093):
Forest.Floor.Load <- c(1.7,15,1.7,8.8,9.8,9.8,8.31,8.31,15.2,6,7.9,1.7,10.9)

Forest.Floor.Load <- Forest.Floor.Load - 0.25 ### subtract average litter load (from 10.1139/cjfr-2016-0475)
Forest.Floor.consump.kg.m2 <- 0.016872*Median.DC^0.71*Forest.Floor.Load^0.671
Forest.Floor.consump.frac <- Forest.Floor.consump.kg.m2/Forest.Floor.Load


# start creating a single list object to encapsulate all the modelling:
#where FFFC is "Forest Floor Fuel Consumption" a la de Groot's naming convention:

FFFC <- as.data.frame(cbind(ecozones.list,Median.DC,Forest.Floor.Load,round(Forest.Floor.consump.kg.m2,digits = 2),round(Forest.Floor.consump.frac,digits = 2)))
names(FFFC) <- c("Ecozone","Median.DC.of.burning","Median.Forest.Floor.Load.kg.m2","Forest.Floor.consump.kg.m2","Forest.Floor.consump.frac")
## for example:
#FFFC$Ecozone.name[1]

### and to query values:
#FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == "BP"]

## TO DO: output a simple table for the above
```

## Constructing fire DMs from abstractions

```{r loadVarDefsSourceSink, echo=FALSE,message=FALSE, warning=FALSE}

#list of ecozone-specific terms (with and without severity dependence)
#first, import blank template that works for a single ecozone:
VarDefs.generic <- as.data.frame(read.csv("~/nrcan-cfs-fire/FireDMs/VarDefsGeneric.csv"))
VarDefs.generic <- VarDefs.generic[,1:7]

#then, replicate for each severity level*ecozone

#use slice from dplyr and each to replicate the template for each ecozone
VarDefs <- VarDefs.generic %>% slice(rep(1:n(), each = length(ecozones.list)))

#fill in ecozone names:
VarDefs$Ecozone <- rep(as.matrix(ecozones.list),times = nrow(VarDefs.generic))

#Once this is done and filled in with data from observations, load the canonical version: 
# this will overwrite the above loop
#NOT RUN (YET)
#VarDefs <- read.csv("~/nrcan-cfs-fire/FireDMs/FireDMTableDefs.csv")




#sink-source DM list:
#first, import blank template that works for a single ecozone:
SourceSinkGeneric <- read.csv("~/nrcan-cfs-fire/FireDMs/SourceSinkGeneric.csv")


#then, replicate for each severity level*ecozone
SourceSink <- SourceSinkGeneric %>% slice(rep(1:n(), each = length(ecozones.list)))

#fill in ecozone names:
SourceSink$Ecozone <- rep(as.matrix(ecozones.list),times = nrow(SourceSinkGeneric))


#Once this is done and filled, load the canonical version: 
# this will overwrite the above loop
#NOT RUN (YET)
#SourceSink <- read.csv("~/FireDMs/SourceSinkLong.csv")


```

First, a generic template for a fire DM is loaded, that can represent any ecozone. It comes in two parts: (1) a list of variables, some biophysical and not relating to fire severity (such as the portion of live branchwood that falls into the smaller size fraction); or (2) severity-specific variables (such as Crown Fraction Burn) for a severity class. The template is loaded, and replicated across the list of ecozones (or any spatial unit) desired. Other processes, such as the analysis of field data, can then be used to fill in ecozone-specific variables in severity classes.

An example of the variable definition template is as follows:

```{r varDefsExample, echo=FALSE, message=FALSE, warning=FALSE}
kbl(head(VarDefs)) %>%
  kable_minimal()  %>%
          kable_styling(latex_options = "scale_down")



```

A plain language name for each variable is provided right in the data, as well.

A second template defines each flux in a Disturbance Matrix, with Source and Sink defined as precise character variables, and a plain language summary ("Process Synonym") included to tie this flux back to language used in the fire science literature. Pseudocode and notes are included in each flux, which is repeated for each fire severity class and ecozone. There are 3900 total fluxes, though many do not have sufficient information to describe differences between ecozones. Many of these are computed automatically, tying back into variables such as Crown Fraction Burned.

```{r SinkSourceExample, echo=FALSE, message=FALSE, warning=FALSE}
kbl(head(SourceSink)) %>%
  kable_minimal() %>%
          kable_styling(latex_options = "scale_down")



```

With both generic ecozone variables as well as severity-specific variables defined and the pseudocode for each flux included, actual DM values are computed as references to tables, subset by ecozone and severity class:

```{r snip2}
#SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 1 & SourceSink$SeverityClass == "Low"] <- 1 - (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])
```


Note that rather than defining softwood crown fraction burned as a variable called "SW.CFB.Boreal.Plains" for each ecozone, there is a row in the VarDefs table that represents SW.CFB in each ecozone and for each severity class, thus avoiding the creation of large lists of manually entered variable names and values in the R environment. Instead, these values can be programmatically entered via external analysis of plot data (not covered here).

```{r DefineDMvalues, echo=FALSE,message=FALSE, warning=FALSE}

j <- 1

for (j in seq(1:length(ecozones.list))) {

  ecozone <- as.character(ecozones.list[j]) #run this loop once for every ecozone

  #print(j)

    
#FluxID: 1
#Source: Softwood (SW) Merch 
#sink: SW Merch
#Plain Language Summary of flux: survival of conifers
#Pseudocode: survival = 1-mortality
#Notes:  by axiom, survival = 1-mortality,

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 1 & SourceSink$SeverityClass == "Low"] <- 1 - (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 1 & SourceSink$SeverityClass == "Mod"] <- 1 - (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 1 & SourceSink$SeverityClass == "High"] <- 1 - (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])

#but, I'm not doing this easily across all three severity classes, no need to run it across each severity class as its own line....

#FluxID: 2
#Source: SW Merch 
#sink: SW Stem Snag
#PLS: Mortality rate of large conifers (includes those with and without burned foliage)
#Pseudocode: as provided from field data, f(ecozone, severity class)
#Notes: mortality >= CFB; may not be the case in extremely fire-tolerant stands, but valid the vast majority of the time
#Notes2: just pulling Softwood CFB 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 2 & SourceSink$SeverityClass == "Low"] <- (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 2 & SourceSink$SeverityClass == "Mod"] <- (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 2 & SourceSink$SeverityClass == "High"] <- (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])

#FluxID: 3
#Source: SW Merch 
#sink: Black Carbon
#PLS: live stemwood to black carbon
#Pseudocode: =0, since no live stemwood -> 0 BC
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 3 & SourceSink$SeverityClass == "Low"] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 3 & SourceSink$SeverityClass == "Mod"] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 3 & SourceSink$SeverityClass == "High"] <- 0


#FluxID: 4
#Source: SW Foliage
#sink: SW Foliage
#PLS: Green fraction of canopy remaining intact after fire
#Pseudocode: IF([(1-Mortality)-CFB]<0,0,[(1-Mortality)-CFB])
#Notes: have to use logical statement here, google sheets version said 1-Mortality, but can be <0 unless logic is enforced here
#note2: given definition of CFB, this includes all foliage in merch and submerch

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 4 & SourceSink$SeverityClass == "Low"] <- ifelse((1 - (VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])) - (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]) < 0,0,(1 - (VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])) - (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])) 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 4 & SourceSink$SeverityClass == "Mod"] <- ifelse((1 - (VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])) - (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]) < 0,0,(1 - (VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])) - (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])) 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 4 & SourceSink$SeverityClass == "High"] <- ifelse((1 - (VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])) - (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]) < 0,0,(1 - (VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])) - (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])) 

#FluxID: 5
#Source: SW Foliage
#sink: Above Ground Very Fast soil C
#PLS: Post-fire litterfall (heat-killed but not burned, then falls to ground within the season)
#Pseudocode: Mortality-CFB
#Notes: assume 100% of heat-killed litter falls within the year of fire

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 5 & SourceSink$SeverityClass == "Low"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"] - VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 5 & SourceSink$SeverityClass == "Mod"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"] - VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 5 & SourceSink$SeverityClass == "High"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"] - VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]

#FluxID: 6
#Source: SW Foliage
#sink: CO2
#PLS: CO2 emission from Crown Fraction Burned
#Pseudocode: CFB*FlamingCO2
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 6 & SourceSink$SeverityClass == "Low"] <- global.vars$FlamingCO2 *  VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 6 & SourceSink$SeverityClass == "Mod"] <- global.vars$FlamingCO2 *  VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 6 & SourceSink$SeverityClass == "High"] <- global.vars$FlamingCO2 *  VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]

#FluxID: 7
#Source: SW Foliage
#sink: CH4
#PLS: CH4 emission from Crown Fraction Burned
#Pseudocode: CFB*FlamingCH4
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 7 & SourceSink$SeverityClass == "Low"] <- global.vars$FlamingCH4 *  VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 7 & SourceSink$SeverityClass == "Mod"] <- global.vars$FlamingCH4 *  VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 7 & SourceSink$SeverityClass == "High"] <- global.vars$FlamingCH4 *  VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]

#FluxID: 8
#Source: SW Foliage
#sink: CO
#PLS: CO emission from Crown Fraction Burned
#Pseudocode: CFB*FlamingCO
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 8 & SourceSink$SeverityClass == "Low"] <- global.vars$FlamingCO *  VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 8 & SourceSink$SeverityClass == "Mod"] <- global.vars$FlamingCO *  VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 8 & SourceSink$SeverityClass == "High"] <- global.vars$FlamingCO *  VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]



#FluxID: 10
#Source: SW Other
#sink: SW Branch Snag
#PLS: Portion of "other" pool as killed by fire but otherwise unconsumed branches
#Pseudocode: (CFB * (1-SW.LgBranch.Comb.Frac))*SW.BW.frac.of.other

#Notes:  #since 1-SW.LgBranch.Comb.Frac is the snag creation rate

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "Low"] <- (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"] *
(1 - VarDefs$Value[VarDefs$Variable.Name == "SW.LgBranch.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])) * VarDefs$Value[VarDefs$Variable.Name == "SW.BW.frac.of.other" & VarDefs$Ecozone == ecozone]            

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "Mod"] <- (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"] *
(1 - VarDefs$Value[VarDefs$Variable.Name == "SW.LgBranch.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])) * VarDefs$Value[VarDefs$Variable.Name == "SW.BW.frac.of.other" & VarDefs$Ecozone == ecozone]  

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "High"] <- (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"] *
(1 - VarDefs$Value[VarDefs$Variable.Name == "SW.LgBranch.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])) * VarDefs$Value[VarDefs$Variable.Name == "SW.BW.frac.of.other" & VarDefs$Ecozone == ecozone]   
                                                                                                                      
#FluxID: 11
#Source: SW Other
#sink: CO2
#PLS: Proportional Combustion sum of branches, stumps, small trees and bark (mix of flaming and smouldering)
#Pseudocode:   (Flux10*FlamingCO2)+
# (Stumps.frac.of.other*DOM.Comb.Rate*SmoulderingCO2)+
# (Litter.frac.burned*SmTree.frac.other*FlamingCO2)+
# (Bark.frac.other*Bark.Comb.Frac*FlamingCO2)

#Notes:  works so far and gives reasonable values of ~0.17, 0.19, 0.2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 11 & SourceSink$SeverityClass == "Low"] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "Low"] * global.vars$FlamingCO2 +  
VarDefs$Value[VarDefs$Variable.Name == "SW.stumps.frac.of.other" & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO2 + (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]*VarDefs$Value[VarDefs$Variable.Name == "SW.SmTree.frac.of.other" & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO2) + (VarDefs$Value[VarDefs$Variable.Name == "SW.bark.frac.of.other" & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == "Bark.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"] * global.vars$FlamingCO2)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 11 & SourceSink$SeverityClass == "Mod"] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "Mod"] * global.vars$FlamingCO2 +  
VarDefs$Value[VarDefs$Variable.Name == "SW.stumps.frac.of.other" & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO2 + (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]*VarDefs$Value[VarDefs$Variable.Name == "SW.SmTree.frac.of.other" & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO2) + (VarDefs$Value[VarDefs$Variable.Name == "SW.bark.frac.of.other" & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == "Bark.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"] * global.vars$FlamingCO2)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 11 & SourceSink$SeverityClass == "High"] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "High"] * global.vars$FlamingCO2 +  
VarDefs$Value[VarDefs$Variable.Name == "SW.stumps.frac.of.other" & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO2 + (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]*VarDefs$Value[VarDefs$Variable.Name == "SW.SmTree.frac.of.other" & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO2) + (VarDefs$Value[VarDefs$Variable.Name == "SW.bark.frac.of.other" & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == "Bark.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"] * global.vars$FlamingCO2)

#FluxID: 12
#Source: SW Other
#sink: CH4
#PLS: Proportional Combustion sum of branches, stumps, small trees and bark (mix of flaming and smouldering)
#Pseudocode:   (Flux10*FlamingCH4)+
# (Stumps.frac.of.other*DOM.Comb.Rate*SmoulderingCH4)+
# (Litter.frac.burned*SmTree.frac.other*FlamingCH4)+
# (Bark.frac.other*Bark.Comb.Frac*FlamingCH4)

#Notes:  works so far and gives reasonable values of ~0.017, 0.019, 0.02

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 12 & SourceSink$SeverityClass == "Low"] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "Low"] * global.vars$FlamingCH4 +  
VarDefs$Value[VarDefs$Variable.Name == "SW.stumps.frac.of.other" & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCH4 + (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]*VarDefs$Value[VarDefs$Variable.Name == "SW.SmTree.frac.of.other" & VarDefs$Ecozone == ecozone]*global.vars$FlamingCH4) + (VarDefs$Value[VarDefs$Variable.Name == "SW.bark.frac.of.other" & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == "Bark.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"] * global.vars$FlamingCH4)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 12 & SourceSink$SeverityClass == "Mod"] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "Mod"] * global.vars$FlamingCH4 +  
VarDefs$Value[VarDefs$Variable.Name == "SW.stumps.frac.of.other" & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCH4 + (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]*VarDefs$Value[VarDefs$Variable.Name == "SW.SmTree.frac.of.other" & VarDefs$Ecozone == ecozone]*global.vars$FlamingCH4) + (VarDefs$Value[VarDefs$Variable.Name == "SW.bark.frac.of.other" & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == "Bark.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"] * global.vars$FlamingCH4)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 12 & SourceSink$SeverityClass == "High"] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "High"] * global.vars$FlamingCH4 +  
VarDefs$Value[VarDefs$Variable.Name == "SW.stumps.frac.of.other" & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCH4 + (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]*VarDefs$Value[VarDefs$Variable.Name == "SW.SmTree.frac.of.other" & VarDefs$Ecozone == ecozone]*global.vars$FlamingCH4) + (VarDefs$Value[VarDefs$Variable.Name == "SW.bark.frac.of.other" & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == "Bark.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"] * global.vars$FlamingCH4)

#FluxID: 13
#Source: SW Other
#sink: CO
#PLS: Proportional Combustion sum of branches, stumps, small trees and bark (mix of flaming and smouldering)
#Pseudocode:   (Flux10*FlamingCO)+
# (Stumps.frac.of.other*DOM.Comb.Rate*SmoulderingCO)+
# (Litter.frac.burned*SmTree.frac.other*FlamingCO)+
# (Bark.frac.other*Bark.Comb.Frac*FlamingCO)

#Notes:  works so far 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 13 & SourceSink$SeverityClass == "Low"] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "Low"] * global.vars$FlamingCO +  
VarDefs$Value[VarDefs$Variable.Name == "SW.stumps.frac.of.other" & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO + (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]*VarDefs$Value[VarDefs$Variable.Name == "SW.SmTree.frac.of.other" & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO) + (VarDefs$Value[VarDefs$Variable.Name == "SW.bark.frac.of.other" & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == "Bark.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"] * global.vars$FlamingCO)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 13 & SourceSink$SeverityClass == "Mod"] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "Mod"] * global.vars$FlamingCO +  
VarDefs$Value[VarDefs$Variable.Name == "SW.stumps.frac.of.other" & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO + (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]*VarDefs$Value[VarDefs$Variable.Name == "SW.SmTree.frac.of.other" & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO) + (VarDefs$Value[VarDefs$Variable.Name == "SW.bark.frac.of.other" & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == "Bark.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"] * global.vars$FlamingCO)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 13 & SourceSink$SeverityClass == "High"] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "High"] * global.vars$FlamingCO +  
VarDefs$Value[VarDefs$Variable.Name == "SW.stumps.frac.of.other" & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO + (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]*VarDefs$Value[VarDefs$Variable.Name == "SW.SmTree.frac.of.other" & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO) + (VarDefs$Value[VarDefs$Variable.Name == "SW.bark.frac.of.other" & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == "Bark.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"] * global.vars$FlamingCO)


#FluxID: 9
#Source: SW Other
#sink: SW Other
#PLS: surviving Live branches, stumps, small trees and bark
#Pseudocode: = 1-(consumption + killed of other pool)

#notes: tried this more complex equation previously, without effect.
#(1-(mortality rate of conifers)*branch fraction of "other" pool)+(1-(medium DOM consumption rate)*stump fraction of other pool)+(1-(mortality of small tree conifers in severity class)*small tree fraction of other pool)+(1-CFB*bark fraction of other pool)
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 9 & SourceSink$SeverityClass == "Low"] <- 1 - sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 10 & SourceSink$FluxID <= 13 & SourceSink$SeverityClass == "Low"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 9 & SourceSink$SeverityClass == "Mod"] <- 1 - sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 10 & SourceSink$FluxID <= 13 & SourceSink$SeverityClass == "Mod"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 9 & SourceSink$SeverityClass == "High"] <- 1 - sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 10 & SourceSink$FluxID <= 13 & SourceSink$SeverityClass == "High"])


#FluxID: 14
#Source: SW SubMerch
#sink: SW SubMerch
#PLS: Understory conifer survival rate
#Pseudocode:  =1-(mortality of submerch conifers in severity class) 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 14 & SourceSink$SeverityClass == "Low"] <- 1 - VarDefs$Value[VarDefs$Variable.Name == "SW.SubMerch.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 14 & SourceSink$SeverityClass == "Mod"] <- 1 - VarDefs$Value[VarDefs$Variable.Name == "SW.SubMerch.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 14 & SourceSink$SeverityClass == "High"] <- 1 - VarDefs$Value[VarDefs$Variable.Name == "SW.SubMerch.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]


#FluxID: 15
#Source: SW SubMerch
#sink: SW Branch Snag
#PLS: Understory conifer stems killed but not consumed
#Pseudocode:  = SubMerch mortality, since live understory trees don't get consumed in the fire, 

#notes: submerch trees assumed to not have large enough branches to avoid consumption in fire.  Equal to 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 15 & SourceSink$SeverityClass == "Low"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.SubMerch.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 15 & SourceSink$SeverityClass == "Mod"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.SubMerch.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 15 & SourceSink$SeverityClass == "High"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.SubMerch.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]


#FluxID: 16
#Source: SW SubMerch
#sink: CO2
#PLS: Understory Conifer consumption rate
#Pseudocode:  = 0 !IF! this is only about submerch stems 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 16 & SourceSink$SeverityClass == "Low"] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 16 & SourceSink$SeverityClass == "Mod"] <-0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 16 & SourceSink$SeverityClass == "High"] <- 0

#FluxID: 17
#Source: SW SubMerch
#sink: CH4
#PLS: Understory Conifer consumption rate
#Pseudocode:  = 0 !IF! this is only about submerch stems 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 17 & SourceSink$SeverityClass == "Low"] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 17 & SourceSink$SeverityClass == "Mod"] <-0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 17 & SourceSink$SeverityClass == "High"] <- 0


#FluxID: 18
#Source: SW SubMerch
#sink: CO
#PLS: Understory Conifer consumption rate
#Pseudocode:  = 0 !IF! this is only about submerch stems 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 18 & SourceSink$SeverityClass == "Low"] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 18 & SourceSink$SeverityClass == "Mod"] <-0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 18 & SourceSink$SeverityClass == "High"] <- 0

#FluxID: 19
#Source: SW Coarse roots
#sink: SW Coarse roots
#PLS: Surviving coarse roots in conifers
#Pseudocode:  =1-(conifer mortality rate)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 19 & SourceSink$SeverityClass == "Low"] <- 1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 19 & SourceSink$SeverityClass == "Mod"] <- 1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 19 & SourceSink$SeverityClass == "High"] <- 1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]

#FluxID: 20
#Source: SW Coarse roots
#sink: Above Ground Fast soil C
#PLS: Coarse Roots killed in fire but not combusted in organic soil
#Pseudocode:  =(conifer mortality rate)*(conifer coarse root fraction in organic soil)
#Note: assuming even if duff burns, coarse live roots don't burn alongsides SW.prop.Coarse.Root.duff

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 20 & SourceSink$SeverityClass == "Low"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"] * VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Coarse.Root.duff" & VarDefs$Ecozone == ecozone]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 20 & SourceSink$SeverityClass == "Mod"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"] * VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Coarse.Root.duff" & VarDefs$Ecozone == ecozone]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 20 & SourceSink$SeverityClass == "High"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"] * VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Coarse.Root.duff" & VarDefs$Ecozone == ecozone]


#FluxID: 21
#Source: SW Coarse roots
#sink: Below Ground Fast soil C
#PLS: Coarse Roots killed in fire but not combusted since they are in mineral soil
#Pseudocode:  =(conifer mortality rate)*(conifer coarse root fraction in mineral soil)
#Note: assuming even if duff burns, coarse live roots don't burn alongsides SW.prop.Coarse.Root.duff

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 21 & SourceSink$SeverityClass == "Low"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"] * (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Coarse.Root.duff" & VarDefs$Ecozone == ecozone])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 21 & SourceSink$SeverityClass == "Mod"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"] * (1 -  VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Coarse.Root.duff" & VarDefs$Ecozone == ecozone])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 21 & SourceSink$SeverityClass == "High"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"] * (1 -  VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Coarse.Root.duff" & VarDefs$Ecozone == ecozone])



#FluxID: 23
#Source: SW fine roots
#sink: Above Ground Very Fast soil C
#PLS: Fine roots killed but not burned in organic soil
#Pseudocode:  =(conifer mortality rate)*(fine root fraction in organic soil)*(1-fraction of duff consumed)
#notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 23 & SourceSink$SeverityClass == "Low"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"] * VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(1 - as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]))

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 23 & SourceSink$SeverityClass == "Mod"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"] * VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(1 - as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]))

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 23 & SourceSink$SeverityClass == "High"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"] * VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(1 - as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]))


#FluxID: 24
#Source: SW fine roots
#sink: Below Ground Very Fast soil C
#PLS: Fine roots killed but not burned in mineral soil
#Pseudocode:  =(conifer mortality rate)*(fine root fraction in mineral soil)
#notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 24 & SourceSink$SeverityClass == "Low"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"] * (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 24 & SourceSink$SeverityClass == "Mod"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"] * (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 24 & SourceSink$SeverityClass == "High"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"] * (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone])




#FluxID: 25
#Source: SW fine roots
#sink: CO2
#PLS: Fine roots combusted in duff
#Pseudocode:  =(conifer mortality rate)*(fine root fraction in organic soil)*(1-fraction of duff consumed)
#notes: since this is solely based on FFFC fraction, which isn't itself severity driven, there's no severity gradient in here.  Note also no relation to SW mortality (since you can burn off roots and not actually kill the tree, to a point)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 25 & SourceSink$SeverityClass == "Low"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 25 & SourceSink$SeverityClass == "Mod"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 25 & SourceSink$SeverityClass == "High"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO2


#FluxID: 26
#Source: SW fine roots
#sink: CH4
#PLS: Fine roots combusted in duff
#Pseudocode:  =(conifer mortality rate)*(fine root fraction in organic soil)*(1-fraction of duff consumed)
#notes: since this is solely based on FFFC fraction, which isn't itself severity driven, there's no severity gradient in here.  Note also no relation to SW mortality (since you can burn off roots and not actually kill the tree, to a point)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 26 & SourceSink$SeverityClass == "Low"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 26 & SourceSink$SeverityClass == "Mod"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 26 & SourceSink$SeverityClass == "High"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCH4



#FluxID: 27
#Source: SW fine roots
#sink: CO
#PLS: Fine roots combusted in duff
#Pseudocode:  =(conifer mortality rate)*(fine root fraction in organic soil)*(1-fraction of duff consumed)
#notes: since this is solely based on FFFC fraction, which isn't itself severity driven, there's no severity gradient in here.  Note also no relation to SW mortality (since you can burn off roots and not actually kill the tree, to a point)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 27 & SourceSink$SeverityClass == "Low"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 27 & SourceSink$SeverityClass == "Mod"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 27 & SourceSink$SeverityClass == "High"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO



#FluxID: 22
#Source: SW fine roots
#sink: SW fine roots
#PLS: Surviving fine roots
#Pseudocode:  =1-(combustion rate of fine roots+mortality rate of fine roots)
#notes: computed at end of fine roots calculations, even though listed as Flux 22
# NOTE: debug needed on high severity, giving value of -0.002, so rounding problem??

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 22 & SourceSink$SeverityClass == "Low"] <- 1 - sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 23 & SourceSink$FluxID <= 27 & SourceSink$SeverityClass == "Low"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 22 & SourceSink$SeverityClass == "Mod"] <- 1 - sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 23 & SourceSink$FluxID <= 27 & SourceSink$SeverityClass == "Mod"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 22 & SourceSink$SeverityClass == "High"] <- 1 - sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 23 & SourceSink$FluxID <= 27 & SourceSink$SeverityClass == "High"])





#Fluxes 28:54 Hardwoods
### HARDWOODS!!!!
###


#FluxID: 28
#Source: HW Merch 
#sink: HW Merch
#Plain Language Summary of flux: survival of conifers
#Pseudocode: survival = 1-mortality
#Notes:  by axiom, survival = 1-mortality,

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 28 & SourceSink$SeverityClass == "Low"] <- 1 - (VarDefs$Value[VarDefs$Variable.Name == "HW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 28 & SourceSink$SeverityClass == "Mod"] <- 1 - (VarDefs$Value[VarDefs$Variable.Name == "HW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 28 & SourceSink$SeverityClass == "High"] <- 1 - (VarDefs$Value[VarDefs$Variable.Name == "HW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])



#FluxID: 29
#Source: HW Merch 
#sink: HW Stem Snag
#PLS: Mortality rate of large broadleaf (includes those with and without burned foliage)
#Pseudocode: as provided from field data, f(ecozone, severity class)
#Notes: mortality >= CFB; may not be the case in extremely fire-tolerant stands, but valid the vast majority of the time
#Notes2: just pulling Softwood CFB 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 29 & SourceSink$SeverityClass == "Low"] <- (VarDefs$Value[VarDefs$Variable.Name == "HW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 29 & SourceSink$SeverityClass == "Mod"] <- (VarDefs$Value[VarDefs$Variable.Name == "HW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 29 & SourceSink$SeverityClass == "High"] <- (VarDefs$Value[VarDefs$Variable.Name == "HW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])

#FluxID: 30
#Source: HW Merch 
#sink: Black Carbon
#PLS: live stemwood to black carbon
#Pseudocode: =0, since no live stemwood -> 0 BC
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 30 & SourceSink$SeverityClass == 'Low'] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 30 & SourceSink$SeverityClass == 'Mod'] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 30 & SourceSink$SeverityClass == 'High'] <- 0


#FluxID: 31
#Source: HW Foliage
#sink: HW Foliage
#PLS: Green fraction of canopy remaining intact after fire
#Pseudocode: IF([(1-Mortality)-CFB]<0,0,[(1-Mortality)-CFB])
#Notes: have to use logical statement here, google sheets version said 1-Mortality, but can be <0 unless logic is enforced here
#note2: given definition of CFB, this includes all foliage in merch and submerch

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 31 & SourceSink$SeverityClass == 'Low'] <- ifelse((1 - (VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'])) - (VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']) < 0,0,(1 - (VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'])) - (VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'])) 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 31 & SourceSink$SeverityClass == 'Mod'] <- ifelse((1 - (VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'])) - (VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']) < 0,0,(1 - (VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'])) - (VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'])) 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 31 & SourceSink$SeverityClass == 'High'] <- ifelse((1 - (VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'])) - (VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']) < 0,0,(1 - (VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'])) - (VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'])) 

#FluxID: 32
#Source: HW Foliage
#sink: Above Ground Very Fast soil C
#PLS: Post-fire litterfall (heat-killed but not burned, then falls to ground within the season)
#Pseudocode: Mortality-CFB
#Notes: assume 100% of heat-killed litter falls within the year of fire

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 32 & SourceSink$SeverityClass == 'Low'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'] - VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 32 & SourceSink$SeverityClass == 'Mod'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'] - VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 32 & SourceSink$SeverityClass == 'High'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'] - VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']

#FluxID: 33
#Source: HW Foliage
#sink: CO2
#PLS: CO2 emission from Crown Fraction Burned
#Pseudocode: CFB*FlamingCO2
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 33 & SourceSink$SeverityClass == 'Low'] <- global.vars$FlamingCO2 *  VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 33 & SourceSink$SeverityClass == 'Mod'] <- global.vars$FlamingCO2 *  VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 33 & SourceSink$SeverityClass == 'High'] <- global.vars$FlamingCO2 *  VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']

#FluxID: 34
#Source: HW Foliage
#sink: CH4
#PLS: CH4 emission from Crown Fraction Burned
#Pseudocode: CFB*FlamingCH4
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 34 & SourceSink$SeverityClass == 'Low'] <- global.vars$FlamingCH4 *  VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 34 & SourceSink$SeverityClass == 'Mod'] <- global.vars$FlamingCH4 *  VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 34 & SourceSink$SeverityClass == 'High'] <- global.vars$FlamingCH4 *  VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']

#FluxID: 35
#Source: HW Foliage
#sink: CO
#PLS: CO emission from Crown Fraction Burned
#Pseudocode: CFB*FlamingCO
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 35 & SourceSink$SeverityClass == 'Low'] <- global.vars$FlamingCO *  VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 35 & SourceSink$SeverityClass == 'Mod'] <- global.vars$FlamingCO *  VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 35 & SourceSink$SeverityClass == 'High'] <- global.vars$FlamingCO *  VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']



#FluxID: 37
#Source: HW Other
#sink: HW Branch Snag
#PLS: Portion of 'other' pool as killed by fire but otherwise unconsumed branches
#Pseudocode: (CFB * (1-HW.LgBranch.Comb.Frac))*HW.BW.frac.of.other

#Notes:  #since 1-HW.LgBranch.Comb.Frac is the snag creation rate

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'Low'] <- (VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'] *
                                                                                                                    (1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.LgBranch.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'])) * VarDefs$Value[VarDefs$Variable.Name == 'HW.BW.frac.of.other' & VarDefs$Ecozone == ecozone]            

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'Mod'] <- (VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'] *
                                                                                                                    (1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.LgBranch.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'])) * VarDefs$Value[VarDefs$Variable.Name == 'HW.BW.frac.of.other' & VarDefs$Ecozone == ecozone]  

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'High'] <- (VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'] *
                                                                                                                     (1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.LgBranch.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'])) * VarDefs$Value[VarDefs$Variable.Name == 'HW.BW.frac.of.other' & VarDefs$Ecozone == ecozone]   

#FluxID: 38
#Source: HW Other
#sink: CO2
#PLS: Proportional Combustion sum of branches, stumps, small trees and bark (mix of flaming and smouldering)
#Pseudocode:   (Flux10*FlamingCO2)+
# (Stumps.frac.of.other*DOM.Comb.Rate*SmoulderingCO2)+
# (Litter.frac.burned*SmTree.frac.other*FlamingCO2)+
# (Bark.frac.other*Bark.Comb.Frac*FlamingCO2)

#Notes:  works so far and gives reasonable values of ~0.17, 0.19, 0.2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 38 & SourceSink$SeverityClass == 'Low'] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'Low'] * global.vars$FlamingCO2 +  
  VarDefs$Value[VarDefs$Variable.Name == 'HW.stumps.frac.of.other' & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO2 + (VarDefs$Value[VarDefs$Variable.Name == 'Unburned.litter.area' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']*VarDefs$Value[VarDefs$Variable.Name == 'HW.SmTree.frac.of.other' & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO2) + (VarDefs$Value[VarDefs$Variable.Name == 'HW.bark.frac.of.other' & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == 'Bark.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'] * global.vars$FlamingCO2)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 38 & SourceSink$SeverityClass == 'Mod'] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'Mod'] * global.vars$FlamingCO2 +  
  VarDefs$Value[VarDefs$Variable.Name == 'HW.stumps.frac.of.other' & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO2 + (VarDefs$Value[VarDefs$Variable.Name == 'Unburned.litter.area' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']*VarDefs$Value[VarDefs$Variable.Name == 'HW.SmTree.frac.of.other' & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO2) + (VarDefs$Value[VarDefs$Variable.Name == 'HW.bark.frac.of.other' & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == 'Bark.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'] * global.vars$FlamingCO2)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 38 & SourceSink$SeverityClass == 'High'] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'High'] * global.vars$FlamingCO2 +  
  VarDefs$Value[VarDefs$Variable.Name == 'HW.stumps.frac.of.other' & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO2 + (VarDefs$Value[VarDefs$Variable.Name == 'Unburned.litter.area' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']*VarDefs$Value[VarDefs$Variable.Name == 'HW.SmTree.frac.of.other' & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO2) + (VarDefs$Value[VarDefs$Variable.Name == 'HW.bark.frac.of.other' & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == 'Bark.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'] * global.vars$FlamingCO2)

#FluxID: 39
#Source: HW Other
#sink: CH4
#PLS: Proportional Combustion sum of branches, stumps, small trees and bark (mix of flaming and smouldering)
#Pseudocode:   (Flux10*FlamingCH4)+
# (Stumps.frac.of.other*DOM.Comb.Rate*SmoulderingCH4)+
# (Litter.frac.burned*SmTree.frac.other*FlamingCH4)+
# (Bark.frac.other*Bark.Comb.Frac*FlamingCH4)

#Notes:  works so far and gives reasonable values of ~0.017, 0.019, 0.02

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 39 & SourceSink$SeverityClass == 'Low'] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'Low'] * global.vars$FlamingCH4 +  
  VarDefs$Value[VarDefs$Variable.Name == 'HW.stumps.frac.of.other' & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCH4 + (VarDefs$Value[VarDefs$Variable.Name == 'Unburned.litter.area' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']*VarDefs$Value[VarDefs$Variable.Name == 'HW.SmTree.frac.of.other' & VarDefs$Ecozone == ecozone]*global.vars$FlamingCH4) + (VarDefs$Value[VarDefs$Variable.Name == 'HW.bark.frac.of.other' & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == 'Bark.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'] * global.vars$FlamingCH4)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 39 & SourceSink$SeverityClass == 'Mod'] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'Mod'] * global.vars$FlamingCH4 +  
  VarDefs$Value[VarDefs$Variable.Name == 'HW.stumps.frac.of.other' & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCH4 + (VarDefs$Value[VarDefs$Variable.Name == 'Unburned.litter.area' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']*VarDefs$Value[VarDefs$Variable.Name == 'HW.SmTree.frac.of.other' & VarDefs$Ecozone == ecozone]*global.vars$FlamingCH4) + (VarDefs$Value[VarDefs$Variable.Name == 'HW.bark.frac.of.other' & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == 'Bark.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'] * global.vars$FlamingCH4)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 39 & SourceSink$SeverityClass == 'High'] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'High'] * global.vars$FlamingCH4 +  
  VarDefs$Value[VarDefs$Variable.Name == 'HW.stumps.frac.of.other' & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCH4 + (VarDefs$Value[VarDefs$Variable.Name == 'Unburned.litter.area' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']*VarDefs$Value[VarDefs$Variable.Name == 'HW.SmTree.frac.of.other' & VarDefs$Ecozone == ecozone]*global.vars$FlamingCH4) + (VarDefs$Value[VarDefs$Variable.Name == 'HW.bark.frac.of.other' & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == 'Bark.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'] * global.vars$FlamingCH4)

#FluxID: 40
#Source: HW Other
#sink: CO
#PLS: Proportional Combustion sum of branches, stumps, small trees and bark (mix of flaming and smouldering)
#Pseudocode:   (Flux10*FlamingCO)+
# (Stumps.frac.of.other*DOM.Comb.Rate*SmoulderingCO)+
# (Litter.frac.burned*SmTree.frac.other*FlamingCO)+
# (Bark.frac.other*Bark.Comb.Frac*FlamingCO)

#Notes:  works so far 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 40 & SourceSink$SeverityClass == 'Low'] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'Low'] * global.vars$FlamingCO +  
  VarDefs$Value[VarDefs$Variable.Name == 'HW.stumps.frac.of.other' & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO + (VarDefs$Value[VarDefs$Variable.Name == 'Unburned.litter.area' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']*VarDefs$Value[VarDefs$Variable.Name == 'HW.SmTree.frac.of.other' & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO) + (VarDefs$Value[VarDefs$Variable.Name == 'HW.bark.frac.of.other' & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == 'Bark.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'] * global.vars$FlamingCO)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 40 & SourceSink$SeverityClass == 'Mod'] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'Mod'] * global.vars$FlamingCO +  
  VarDefs$Value[VarDefs$Variable.Name == 'HW.stumps.frac.of.other' & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO + (VarDefs$Value[VarDefs$Variable.Name == 'Unburned.litter.area' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']*VarDefs$Value[VarDefs$Variable.Name == 'HW.SmTree.frac.of.other' & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO) + (VarDefs$Value[VarDefs$Variable.Name == 'HW.bark.frac.of.other' & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == 'Bark.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'] * global.vars$FlamingCO)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 40 & SourceSink$SeverityClass == 'High'] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'High'] * global.vars$FlamingCO +  
  VarDefs$Value[VarDefs$Variable.Name == 'HW.stumps.frac.of.other' & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO + (VarDefs$Value[VarDefs$Variable.Name == 'Unburned.litter.area' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']*VarDefs$Value[VarDefs$Variable.Name == 'HW.SmTree.frac.of.other' & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO) + (VarDefs$Value[VarDefs$Variable.Name == 'HW.bark.frac.of.other' & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == 'Bark.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'] * global.vars$FlamingCO)


#FluxID: 36
#Source: HW Other
#sink: HW Other
#PLS: surviving Live branches, stumps, small trees and bark
#Pseudocode: = 1-(consumption + killed of other pool)

#notes: tried this more complex equation previously, without effect.
#(1-(mortality rate of conifers)*branch fraction of 'other' pool)+(1-(medium DOM consumption rate)*stump fraction of other pool)+(1-(mortality of small tree conifers in severity class)*small tree fraction of other pool)+(1-CFB*bark fraction of other pool)
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 36 & SourceSink$SeverityClass == 'Low'] <- 1 - sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 37 & SourceSink$FluxID <= 40 & SourceSink$SeverityClass == 'Low'])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 36 & SourceSink$SeverityClass == 'Mod'] <- 1 - sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 37 & SourceSink$FluxID <= 40 & SourceSink$SeverityClass == 'Mod'])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 36 & SourceSink$SeverityClass == 'High'] <- 1 - sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 37 & SourceSink$FluxID <= 40 & SourceSink$SeverityClass == 'High'])


#FluxID: 41
#Source: HW SubMerch
#sink: HW SubMerch
#PLS: Understory conifer survival rate
#Pseudocode:  =1-(mortality of submerch conifers in severity class) 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 41 & SourceSink$SeverityClass == 'Low'] <- 1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.SubMerch.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 41 & SourceSink$SeverityClass == 'Mod'] <- 1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.SubMerch.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 41 & SourceSink$SeverityClass == 'High'] <- 1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.SubMerch.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']


#FluxID: 42
#Source: HW SubMerch
#sink: HW Branch Snag
#PLS: Understory conifer stems killed but not consumed
#Pseudocode:  = SubMerch mortality, since live understory trees don't get consumed in the fire, 

#notes: submerch trees assumed to not have large enough branches to avoid consumption in fire.  Equal to 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 42 & SourceSink$SeverityClass == 'Low'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.SubMerch.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 42 & SourceSink$SeverityClass == 'Mod'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.SubMerch.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 42 & SourceSink$SeverityClass == 'High'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.SubMerch.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']


#FluxID: 43
#Source: HW SubMerch
#sink: CO2
#PLS: Understory Conifer consumption rate
#Pseudocode:  = 0 !IF! this is only about submerch stems 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 43 & SourceSink$SeverityClass == 'Low'] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 43 & SourceSink$SeverityClass == 'Mod'] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 43 & SourceSink$SeverityClass == 'High'] <- 0

#FluxID: 44
#Source: HW SubMerch
#sink: CH4
#PLS: Understory Conifer consumption rate
#Pseudocode:  = 0 !IF! this is only about submerch stems 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 44 & SourceSink$SeverityClass == 'Low'] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 44 & SourceSink$SeverityClass == 'Mod'] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 44 & SourceSink$SeverityClass == 'High'] <- 0


#FluxID: 45
#Source: HW SubMerch
#sink: CO
#PLS: Understory Conifer consumption rate
#Pseudocode:  = 0 !IF! this is only about submerch stems 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 45 & SourceSink$SeverityClass == 'Low'] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 45 & SourceSink$SeverityClass == 'Mod'] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 45 & SourceSink$SeverityClass == 'High'] <- 0

#FluxID: 46
#Source: HW Coarse roots
#sink: HW Coarse roots
#PLS: Surviving coarse roots in conifers
#Pseudocode:  =1-(conifer mortality rate)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 46 & SourceSink$SeverityClass == 'Low'] <- 1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 46 & SourceSink$SeverityClass == 'Mod'] <- 1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 46 & SourceSink$SeverityClass == 'High'] <- 1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']

#FluxID: 47
#Source: HW Coarse roots
#sink: Above Ground Fast soil C
#PLS: Coarse Roots killed in fire but not combusted in organic soil
#Pseudocode:  =(conifer mortality rate)*(conifer coarse root fraction in organic soil)
#Note: assuming even if duff burns, coarse live roots don't burn alongsides HW.prop.Coarse.Root.duff

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 47 & SourceSink$SeverityClass == 'Low'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'] * VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Coarse.Root.duff' & VarDefs$Ecozone == ecozone]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 47 & SourceSink$SeverityClass == 'Mod'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'] * VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Coarse.Root.duff' & VarDefs$Ecozone == ecozone]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 47 & SourceSink$SeverityClass == 'High'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'] * VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Coarse.Root.duff' & VarDefs$Ecozone == ecozone]


#FluxID: 48
#Source: HW Coarse roots
#sink: Below Ground Fast soil C
#PLS: Coarse Roots killed in fire but not combusted since they are in mineral soil
#Pseudocode:  =(conifer mortality rate)*(conifer coarse root fraction in mineral soil)
#Note: assuming even if duff burns, coarse live roots don't burn alongsides HW.prop.Coarse.Root.duff

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 48 & SourceSink$SeverityClass == 'Low'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'] * (1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Coarse.Root.duff' & VarDefs$Ecozone == ecozone])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 48 & SourceSink$SeverityClass == 'Mod'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'] * (1 -  VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Coarse.Root.duff' & VarDefs$Ecozone == ecozone])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 48 & SourceSink$SeverityClass == 'High'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'] * (1 -  VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Coarse.Root.duff' & VarDefs$Ecozone == ecozone])




#FluxID: 50
#Source: HW fine roots
#sink: Above Ground Very Fast soil C
#PLS: Fine roots killed but not burned in organic soil
#Pseudocode:  =(conifer mortality rate)*(fine root fraction in organic soil)*(1-fraction of duff consumed)
#notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 50 & SourceSink$SeverityClass == 'Low'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'] * VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(1 - as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]))

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 50 & SourceSink$SeverityClass == 'Mod'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'] * VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(1 - as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]))

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 50 & SourceSink$SeverityClass == 'High'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'] * VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(1 - as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]))


#FluxID: 51
#Source: HW fine roots
#sink: Below Ground Very Fast soil C
#PLS: Fine roots killed but not burned in mineral soil
#Pseudocode:  =(conifer mortality rate)*(fine root fraction in mineral soil)
#notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 51 & SourceSink$SeverityClass == 'Low'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'] * (1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 51 & SourceSink$SeverityClass == 'Mod'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'] * (1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 51 & SourceSink$SeverityClass == 'High'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'] * (1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone])




#FluxID: 52
#Source: HW fine roots
#sink: CO2
#PLS: Fine roots combusted in duff
#Pseudocode:  =(conifer mortality rate)*(fine root fraction in organic soil)*(1-fraction of duff consumed)
#notes: since this is solely based on FFFC fraction, which isn't itself severity driven, there's no severity gradient in here.  Note also no relation to HW mortality (since you can burn off roots and not actually kill the tree, to a point)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 52 & SourceSink$SeverityClass == 'Low'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 52 & SourceSink$SeverityClass == 'Mod'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 52 & SourceSink$SeverityClass == 'High'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO2


#FluxID: 53
#Source: HW fine roots
#sink: CH4
#PLS: Fine roots combusted in duff
#Pseudocode:  =(conifer mortality rate)*(fine root fraction in organic soil)*(1-fraction of duff consumed)
#notes: since this is solely based on FFFC fraction, which isn't itself severity driven, there's no severity gradient in here.  Note also no relation to HW mortality (since you can burn off roots and not actually kill the tree, to a point)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 53 & SourceSink$SeverityClass == 'Low'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 53 & SourceSink$SeverityClass == 'Mod'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 53 & SourceSink$SeverityClass == 'High'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCH4



#FluxID: 54
#Source: HW fine roots
#sink: CO
#PLS: Fine roots combusted in duff
#Pseudocode:  =(conifer mortality rate)*(fine root fraction in organic soil)*(1-fraction of duff consumed)
#notes: since this is solely based on FFFC fraction, which isn't itself severity driven, there's no severity gradient in here.  Note also no relation to HW mortality (since you can burn off roots and not actually kill the tree, to a point)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 54 & SourceSink$SeverityClass == 'Low'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 54 & SourceSink$SeverityClass == 'Mod'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 54 & SourceSink$SeverityClass == 'High'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO



#FluxID: 49
#Source: HW fine roots
#sink: HW fine roots
#PLS: Surviving fine roots
#Pseudocode:  =1-(combustion rate of fine roots+mortality rate of fine roots)
#notes: computed at end of fine roots calculations, even though listed as Flux 22
# NOTE: debug needed on high severity, giving value of -0.002, so rounding problem??

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 49 & SourceSink$SeverityClass == 'Low'] <- 1 - sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 50 & SourceSink$FluxID <= 54 & SourceSink$SeverityClass == 'Low'])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 49 & SourceSink$SeverityClass == 'Mod'] <- 1 - sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 50 & SourceSink$FluxID <= 54 & SourceSink$SeverityClass == 'Mod'])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 49 & SourceSink$SeverityClass == 'High'] <- 1 - sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 50 & SourceSink$FluxID <= 54 & SourceSink$SeverityClass == 'High'])



### end hardwoods


#FluxID: 55
#Source: Aboveground Very Fast DOM
#sink: Aboveground Very Fast DOM
#PLS: Unburned fraction of The L horizonb comprised of foliar litter plus dead fine roots, approximately <5 mm diameter
#Pseudocode:  =Unburned.litter.area(from plot data)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 55 & SourceSink$SeverityClass == "Low"] <-  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 55 & SourceSink$SeverityClass == "Mod"] <-  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 55 & SourceSink$SeverityClass == "High"] <-  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]


#FluxID: 56
#Source: Aboveground Very Fast DOM
#sink: CO2
#PLS: Burned fraction of The L horizonb comprised of foliar litter plus dead fine roots, approximately <5 mm diameter
#Pseudocode:  =1-Unburned.litter.area(from plot data)*Flaming

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 56 & SourceSink$SeverityClass == "Low"] <- (1 -  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])*global.vars$FlamingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 56 & SourceSink$SeverityClass == "Mod"] <- (1 -  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])*global.vars$FlamingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 56 & SourceSink$SeverityClass == "High"] <- (1 -  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])*global.vars$FlamingCO2


#FluxID: 57
#Source: Aboveground Very Fast DOM
#sink: CH4
#PLS: Burned fraction of The L horizonb comprised of foliar litter plus dead fine roots, approximately <5 mm diameter
#Pseudocode:  =1-Unburned.litter.area(from plot data)*Flaming

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 57 & SourceSink$SeverityClass == "Low"] <- (1 -  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])*global.vars$FlamingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 57 & SourceSink$SeverityClass == "Mod"] <- (1 -  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])*global.vars$FlamingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 57 & SourceSink$SeverityClass == "High"] <- (1 -  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])*global.vars$FlamingCH4


#FluxID: 58
#Source: Aboveground Very Fast DOM
#sink: CO
#PLS: Burned fraction of The L horizonb comprised of foliar litter plus dead fine roots, approximately <5 mm diameter
#Pseudocode:  =1-Unburned.litter.area(from plot data)*Flaming

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 58 & SourceSink$SeverityClass == "Low"] <- (1 -  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])*global.vars$FlamingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 58 & SourceSink$SeverityClass == "Mod"] <- (1 -  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])*global.vars$FlamingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 58 & SourceSink$SeverityClass == "High"] <- (1 -  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])*global.vars$FlamingCO


#FluxID: 59
#Source: Belowground Very Fast DOM
#sink: Belowground Very Fast Soil C
#PLS: Uncombusted Fraction of Dead fine roots in the mineral soil, approximately <5 mm diameter
#Pseudocode:  == 1, since dead roots in the mineral soil are not combusted

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 59 & SourceSink$SeverityClass == "Low"] <- 1 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 59 & SourceSink$SeverityClass == "Mod"] <- 1

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 59 & SourceSink$SeverityClass == "High"] <- 1

#FluxID: 60
#Source: Aboveground Fast DOM
#sink: Above Ground Fast soil C
#PLS: Uncombusted Fine and small woody debris plus dead coarse roots in the forest floor, approximately 5 and <75 mm diameter
#Pseudocode: =[(litter surface area fraction unburned*woody debris portion of AGFastDOM)+(Dead coarse root fraction of AGFastDOM*(fraction of duff consumed)]
#*Assume all woody fine+small woody debris is combusted, but only fractional combustion of dead coarse roots alongside duff
#CWD.frac.of.AGFastDOM

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "Low"] <- (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]*VarDefs$Value[VarDefs$Variable.Name == "CWD.frac.of.AGFastDOM" & VarDefs$Ecozone == ecozone] + ((1 - VarDefs$Value[VarDefs$Variable.Name == "CWD.frac.of.AGFastDOM" & VarDefs$Ecozone == ecozone])*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]))))

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "Mod"] <-  (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]*VarDefs$Value[VarDefs$Variable.Name == "CWD.frac.of.AGFastDOM" & VarDefs$Ecozone == ecozone] + ((1 - VarDefs$Value[VarDefs$Variable.Name == "CWD.frac.of.AGFastDOM" & VarDefs$Ecozone == ecozone])*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]))))

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "High"] <- (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]*VarDefs$Value[VarDefs$Variable.Name == "CWD.frac.of.AGFastDOM" & VarDefs$Ecozone == ecozone] + ((1 - VarDefs$Value[VarDefs$Variable.Name == "CWD.frac.of.AGFastDOM" & VarDefs$Ecozone == ecozone])*(as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]))))


#FluxID: 61
#Source: Aboveground Fast DOM
#sink: CO2
#PLS: Combusted Fine and small woody debris plus dead coarse roots in the forest floor, approximately 5 and <75 mm diameter
#Pseudocode: = flux60*smouldering


SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 61 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "Low"])*global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 61 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "Mod"])*global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 61 & SourceSink$SeverityClass == "High"] <- (1 -  SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "High"])*global.vars$SmoulderingCO2

#FluxID: 62
#Source: Aboveground Fast DOM
#sink: CH4
#PLS: Combusted Fine and small woody debris plus dead coarse roots in the forest floor, approximately 5 and <75 mm diameter
#Pseudocode: = flux60*smouldering


SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 62 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "Low"])*global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 62 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "Mod"])*global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 62 & SourceSink$SeverityClass == "High"] <- (1 -  SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "High"])*global.vars$SmoulderingCH4

#FluxID: 63
#Source: Aboveground Fast DOM
#sink: CO
#PLS: Combusted Fine and small woody debris plus dead coarse roots in the forest floor, approximately 5 and <75 mm diameter
#Pseudocode: = flux60*smouldering


SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 63 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "Low"])*global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 63 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "Mod"])*global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 63 & SourceSink$SeverityClass == "High"] <- (1 -  SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "High"])*global.vars$SmoulderingCO

#FluxID: 64
#Source: Belowground Fast DOM
#sink: Below Ground Fast soil C
#PLS: Uncombusted fraction of Dead coarse roots in the mineral soil, approximately 5 diameter
#Pseudocode: =~ 1, since no combustion within mineral soil

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 64 & SourceSink$SeverityClass == "Low"] <- 1
SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 64 & SourceSink$SeverityClass == "Mod"] <- 1
SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 64 & SourceSink$SeverityClass == "High"] <- 1

#FluxID: 65
#Source: Medium DOM
#sink: Medium Soil C
#PLS: Uncombusted Coarse woody debris on the ground
#Pseudocode: =(1-(fraction of duff consumed))*(1-unburned litter area)
#note: could be from field data, here assuming burns at same rate as duff

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "Low"] <- (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])*(1 - (as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]))) 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "Mod"] <- (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])*(1 - (as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])))

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "High"] <- (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])*(1 - (as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])))


#FluxID: 66
#Source: Medium DOM
#sink: CO2
#PLS: Combusted Coarse woody debris on the ground
#Pseudocode: =(1-(fraction of duff consumed))*(1-unburned litter area)*smouldering
#note: could be from field data, here assuming burns at same rate as duff
#high values are probably on the high end, would need field data

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 66 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "Low"])*global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 66 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "Mod"])*global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 66 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "High"])*global.vars$SmoulderingCO2

#FluxID: 67
#Source: Medium DOM
#sink: CH4
#PLS: Combusted Coarse woody debris on the ground
#Pseudocode: =(1-(fraction of duff consumed))*(1-unburned litter area)*smouldering
#note: could be from field data, here assuming burns at same rate as duff
#high values are probably on the high end, would need field data

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 67 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "Low"])*global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 67 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "Mod"])*global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 67 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "High"])*global.vars$SmoulderingCH4


#FluxID: 68
#Source: Medium DOM
#sink: CO
#PLS: Combusted Coarse woody debris on the ground
#Pseudocode: =(1-(fraction of duff consumed))*(1-unburned litter area)*smouldering
#note: could be from field data, here assuming burns at same rate as duff
#high values are probably on the high end, would need field data

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 68 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "Low"])*global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 68 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "Mod"])*global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 68 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "High"])*global.vars$SmoulderingCO



#FluxID: 69
#Source: Medium DOM
#sink: Black Carbon
#PLS: Coarse woody debris on the ground converted to black carbon
#Pseudocode: =0 (until field data given)
#note: could be from field data, here assuming burns at same rate as duff
#high values are probably on the high end, would need field data (or at least Koroscil MSc lab data)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 69 & SourceSink$SeverityClass == "Low"] <- 0
SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 69 & SourceSink$SeverityClass == "Mod"] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 69 & SourceSink$SeverityClass == "High"] <- 0


#FluxID: 70
#Source: Aboveground Slow DOM
#sink: Above Ground slow soil C
#PLS: Uncombusted fraction of duff horizons
#Pseudocode: =1-(fraction of duff consumed)
#note: see CaMP for slow DOM in peat layers

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "Low"] <- (1 - (as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone]))) 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "Mod"] <- (1 - (as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])))

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "High"] <- (1 - (as.numeric(FFFC$Forest.Floor.consump.frac[FFFC$Ecozone == ecozone])))


#FluxID: 71
#Source: Aboveground Slow DOM
#sink: CO2
#PLS: Combusted Fraction of duff horizons
#Pseudocode: =(fraction of duff consumed)*Smouldering


SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 71 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "Low"])*global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 71 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "Mod"])*global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 71 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "High"])*global.vars$SmoulderingCO2

#FluxID: 72
#Source: Aboveground Slow DOM
#sink: CH4
#PLS: Combusted Fraction of duff horizons
#Pseudocode: ==(fraction of duff consumed)*Smouldering

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 72 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "Low"])*global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 72 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "Mod"])*global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 72 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "High"])*global.vars$SmoulderingCH4


#FluxID: 73
#Source: Aboveground Slow DOM
#sink: CO
#PLS: Combusted Fraction of duff horizons
#Pseudocode: =(fraction of duff consumed)*Smouldering

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 73 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "Low"])*global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 73 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "Mod"])*global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 73 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "High"])*global.vars$SmoulderingCO


#FluxID: 74
#Source: Belowground Slow DOM
#sink: Below Ground Slow soil C
#PLS: Uncombusted fraction of Humified organic matter in the mineral soil
#Pseudocode: ==0
#notes: no combustion 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 74 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "Low"])*global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 74 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "Mod"])*global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 74 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "High"])*global.vars$SmoulderingCO

#FluxID: 75
#Source: Softwood Stem Snag
#sink: Medium Soil C
#PLS: Fraction of conifer snags that fall to ground but not combusted (i.e. fall after the passage of the fire and due to the fire)
#Pseudocode: =[1-(SW.Snag.Comb.Frac]*(Snag.Fall.Frac)
#notes: assumeno combustion of these snags otherwise

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "Low"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]) * VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "Mod"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]) * VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "High"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]) * VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]


#FluxID: 76
#Source: Softwood Stem Snag
#sink: Softwood Stem Snag
#PLS: Uncombusted fraction of conifer snags (still upright)
#Pseudocode: =[1-(SW.Snag.Comb.Frac)]*(1-Snag.Fall.Frac)
#notes: assume no combustion of these snags otherwise

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "Low"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]) * (1 - VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "Mod"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]) * (1 - VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "High"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]) * (1 - VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])

#FluxID: 77
#Source: Softwood Stem Snag
#sink: CO2
#PLS: Uncombusted fraction of conifer snags (still upright)
#Pseudocode: =[1-SW.Snag.Comb.Frac-Snag.Fall.Frac)*Flaming
#notes: assume no combustion of these snags otherwise

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 77 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "Low"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "Low"])*global.vars$FlamingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 77 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "Mod"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "Mod"])*global.vars$FlamingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 77 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "High"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "High"])*global.vars$FlamingCO2

#FluxID: 78
#Source: Softwood Stem Snag
#sink: CH4
#PLS: Uncombusted fraction of conifer snags (still upright)
#Pseudocode: =[1-SW.Snag.Comb.Frac-Snag.Fall.Frac)*Flaming
#notes: snags not remaining upright nor fallen down are combusted

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 78 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "Low"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "Low"])*global.vars$FlamingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 78 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "Mod"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "Mod"])*global.vars$FlamingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 78 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "High"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "High"])*global.vars$FlamingCH4


#FluxID: 79
#Source: Softwood Stem Snag
#sink: CO
#PLS: Uncombusted fraction of conifer snags (still upright)
#Pseudocode: =[1-SW.Snag.Comb.Frac-Snag.Fall.Frac)*SW.Snag.Comb.Frac*Flaming
#notes: snags not remaining upright nor fallen down are combusted

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 79 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "Low"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "Low"])*global.vars$FlamingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 79 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "Mod"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "Mod"])*global.vars$FlamingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 79 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "High"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "High"])*global.vars$FlamingCO

#FluxID: 80
#Source: Softwood Stem Snag
#sink: Black Carbon
#PLS: Uncombusted fraction of conifer snags (still upright)
#Pseudocode: =[1-SW.Snag.Comb.Frac-Snag.Fall.Frac)*BlackCarbon
#notes: no black carbon production for now, will need to estimate based on field data

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 80 & SourceSink$SeverityClass == "Low"] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 80 & SourceSink$SeverityClass == "Mod"] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 80 & SourceSink$SeverityClass == "High"] <- 0


#FluxID: 81
#Source: Softwood Branch Snag
#sink: Above Ground Fast soil C
#PLS: Portion of conifer snag branches that falls onto the ground
#Pseudocode: =[1-(SW.Snag.BW.Comb.Frac)]*Snag.Fall.Frac
#notes: Assuming half of all unconsumed portions branches on snags fall to the ground, half of them remain on the snag.  No field data to this effect.  

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "Low"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.BW.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]) * VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "Mod"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.BW.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]) * VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "High"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.BW.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]) * VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]


#FluxID: 82
#Source: Softwood Branch Snag
#sink: Softwood Branch Snag
#PLS: Unaltered fraction of snag branches
#Pseudocode: =[1-(SW.Snag.BW.Comb.Frac)]*(1-Snag.Fall.Frac)
#notes: Assuming half of all unconsumed portions branches on snags fall to the ground, half of them remain on the snag.  No field data to this effect.  

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "Low"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.BW.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]) * (1 - VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "Mod"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.BW.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]) * (1 - VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "High"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.BW.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]) * (1 - VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])

#FluxID: 83
#Source: Softwood Branch Snag
#sink: CO2
#PLS: Unaltered fraction of snag branches
#Pseudocode: = (SW.Snag.BW.Comb.Frac)*(Snag.Fall.Frac)
#notes: Assuming half of all unconsumed portions branches on snags fall to the ground, half of them remain on the snag.  No field data to this effect.  

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 83 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "Low"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "Low"])*global.vars$FlamingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 83 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "Mod"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "Mod"])*global.vars$FlamingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 83 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "High"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "High"])*global.vars$FlamingCO2


#FluxID: 84
#Source: Softwood Branch Snag
#sink: CH4
#PLS: Unaltered fraction of snag branches
#Pseudocode: = (SW.Snag.BW.Comb.Frac)*(Snag.Fall.Frac)
#notes: Assuming half of all unconsumed portions branches on snags fall to the ground, half of them remain on the snag.  No field data to this effect.  

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 84 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "Low"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "Low"])*global.vars$FlamingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 84 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "Mod"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "Mod"])*global.vars$FlamingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 84 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "High"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "High"])*global.vars$FlamingCH4



#FluxID: 85
#Source: Softwood Branch Snag
#sink: CO
#PLS: Unaltered fraction of snag branches
#Pseudocode: = (SW.Snag.BW.Comb.Frac)*(Snag.Fall.Frac)
#notes: Assuming half of all unconsumed portions branches on snags fall to the ground, half of them remain on the snag.  No field data to this effect.  

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 85 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "Low"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "Low"])*global.vars$FlamingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 85 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "Mod"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "Mod"])*global.vars$FlamingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 85 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "High"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "High"])*global.vars$FlamingCO


## end loop

  # final step in loop: once you have a list each built by ecozone, then build a higher-level list called "FireDM"
   
}
  


```

And make a checksum table to ensure all the major pools sum of up 1:

```{r checkSum, echo=FALSE,message=FALSE, warning=FALSE}
##example calc:
#sum(SourceSink$Value[SourceSink$Ecozone == "BP" & SourceSink$Source == "Softwood Merchantable" & SourceSink$SeverityClass == "Mod"])

source.list.checksum <- c("Softwood Merchantable", "Softwood Foliage","Softwood Other","Softwood Submerchantable", "Softwood Coarse Roots","Softwood Fine Roots","Aboveground Very Fast DOM","Aboveground Fast DOM","Medium DOM","Aboveground Slow DOM","Softwood Stem Snag","Softwood Branch Snag","Hardwood Merchantable", "Hardwood Foliage","Hardwood Other","Hardwood Submerchantable","Hardwood Coarse Roots","Hardwood Fine Roots","Hardwood Stem Snag","Hardwood Branch Snag") 

#checksum for a single ecozone, single severity level:



for (i in seq(1:length(source.list.checksum))) {

  print(source.list.checksum[i])
  print(sum(SourceSink$Value[SourceSink$Ecozone == "BP" & SourceSink$Source == source.list.checksum[i] & SourceSink$SeverityClass == "High"]))
}


```



In a final step, a classical tabular DM is show, with row and column names precisely matching those in the Sink and Source columns in the SourceSink table:

```{r makeTables, echo=FALSE,message=FALSE, warning=FALSE}
 #example of ecozone-specific extraction NOT RUN
  #SourceSink$Value[SourceSink$Ecozone == "BP" & SourceSink$FluxID < 9 & SourceSink$SeverityClass == "Mod"]
  
  # and then do the source as rows and sink as column?
##single cell reference: SourceSink$Value[SourceSink$Ecozone == "BP" & SourceSink$Source == "Softwood Merchantable" & SourceSink$Sink == "Softwood Merchantable" & SourceSink$SeverityClass == "Mod"]
  
  
  ### list for columns and rows in visual DM: can be any order, not linked to FluxID or anything:
  sink.col.list <- c("Softwood Merchantable", "Softwood Stem Snag","Softwood Foliage","Above Ground Very Fast soil C", "CO2", "CH4", "CO")
  source.row.list <- c("Softwood Merchantable", "Softwood Stem Snag","Softwood Foliage","Above Ground Very Fast soil C", "CO2", "CH4", "CO")

  
  ###make this a function with attributes of ecozone and severity class:
  
  DM.temp <- as.data.frame(array(NA,c(length(sink.col.list),length(sink.col.list))))
  
  for (j in seq(1:8)) {
    for (k in seq(1:8)) {
     
      #if the pair is blank, then return NA, otherwise, look through the list of sink/source pairs for the ecozone and severity level and return that value 
      ifelse(is.na(SourceSink$Value[SourceSink$Ecozone == "BP" & SourceSink$Source == source.row.list[j] & SourceSink$Sink == sink.col.list[k] & SourceSink$SeverityClass == "Mod"]),NA,DM.temp[j,k] <- SourceSink$Value[SourceSink$Ecozone == "BP" & SourceSink$Source == source.row.list[j] & SourceSink$Sink == sink.col.list[k] & SourceSink$SeverityClass == "Mod"])
     
      
    }
    
    
  } 
  rownames(DM.temp) <- source.row.list
  kbl(DM.temp[1:length(sink.col.list),1:length(sink.col.list)],col.names = c("Softwood Merchantable", "Softwood Stem Snag","Softwood Foliage","Above Ground Very Fast soil C", "CO2", "CH4", "CO"), align = "c",caption = "Example moderate severity DM in Boreal Plains") %>%
    kable_styling(full_width = F, html_font = "Cambria") %>%
column_spec(2:length(sink.col.list), width = "2cm") %>%
column_spec(1, width = "3cm") %>%
  kableExtra::landscape() %>%
          kable_styling(latex_options = "scale_down")
```
