---
title: Incorporating fire severity for refined carbon emissions estimates of boreal and temperate forest fires in the Generic Carbon Budget Model (GCBM)
journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'gmd')`"
author:
  - given_name: Dan K.
    surname: Thompson
    affiliation: 1
    email: daniel.thompson@nrcan-rncan.gc.ca
    corresponding: true
  - given_name: Ellen
    surname: Whitman
    affiliation: 2
    email: ellen.whitman@nrcan-rncan.gc.ca
  - given_name: Ben
    surname: Hudson
    affiliation: 3
    email: benjamin.hudson@nrcan-rncan.gc.ca
  - given_name: Chelene
    surname: Hanes
    affiliation: 1
    email: chelene.hanes@nrcan-rncan.gc.ca
  - given_name: Vinicius
    surname: Manvailer Goncalves
    affiliation: 3
    email: 
  - given_name: Werner
    surname: Kurz
    affiliation: 3
    email: werner.kurz@nrcan-rncan.gc.ca
    

affiliation:
  - code: 1
    address: Natural Resources Canada, Canadian Forest Service, Great Lakes Forestry Centre, Sault Ste. Marie, Canada
  - code: 2
    address: Natural Resources Canada, Canadian Forest Service, Northern Forestry Centre, Edmonton, Canada
  - code: 3
    address: Natural Resources Canada, Canadian Forest Service, Pacific Forestry Centre, Victoria, Canada

abstract: |
  Wildfire is the most impactful natural disturbance to Canada's boreal and temperate forest biomes.  Current representations of fire impact on forest carbon stocks is limited to a single parameterization of fire severity (i.e. the fraction of biomass consumed) that assumes only high severity fires, despite a large and increasing evidence base of widespread mixed-severity wildfire.  In this submodel of the larger Generic Carbon Budget Model for forest carbon accounting, field measurements of biomass consumption as related to satellite-derived burn severity maps are interpretted from a fire physics and ecology perspective to derive algorithms to describe forest carbon fluxes in the immediate aftermath of fires.  Compared to the baseline high severity-only representation, this mixed severity modelling framework changes modelled total Carbon flux to the atmosphere by [###]%, with the largest changes in [pool].  Per fire energy release rates as detected by satellite yield a favourable rank correlation with this severity-only method, and regional estimates of atmospheric CO release by satellite compare favourably to outputs from this severity-driven model.
bibliography: references.bib
running:
  title: Fire Severity and Forest Carbon Budget Models
  author: Thompson et al.
# This section is mandatory even if you declare that no competing interests are present.
competinginterests: The authors declare no competing interests.
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed. 
# Note: additional copyright statements for affiliated software or data need to be placed in the data availability section. 
copyrightstatement: His Majesty the King in Right of Canada as represented by the Minister of Natural Resources Canada. This work is distributed under the Creative Commons Attribution 4.0 License.
### The following commands are for the statements about the availability of data sets and/or software code corresponding to the manuscript.
### It is strongly recommended to make use of these sections in case data sets and/or software code have been part of your research the article is based on.
### Note: unless stated otherwise, software and data affiliated with the manuscript are assumed to be published under the same licence as the article (currently Creative Commons 4.0)
availability:
  codedata: This article was produced from an RMarkdown document with underlying data, available at https://github.com/nrcan-cfs-fire/FireDMs


authorcontribution: Thompson and Whitman contributed to the concept and code design with the assistance of Hanes, Hudson

disclaimer: The algorithm and results presented only apply to boreal and temperate forest ecosystems where sufficient ground plots of fire severity are available.  As a data-driven model, this framework is not suitable for other ecosystems nor agricultural or forestry biomass burning practices.

acknowledgements: Thanks to (insert names here)

appendix: |
  \section{List of fluxes and corresponding fire-related plain-language summary}
  Regarding figures and tables in appendices, the following two options are possible depending on your general handling of figures and tables in the manuscript environment:
  \subsection{Option 1}
  If you sorted all figures and tables into the sections of the text, please also sort the appendix figures and appendix tables into the respective appendix sections.
  They will be correctly named automatically.
  \subsection{Option 2}
  If you put all figures after the reference list, please insert appendix tables and figures after the normal tables and figures.
  
  To rename them correctly to A1, A2, etc., please add the following commands in front of them:
  `\appendixfigures` needs to be added in front of appendix figures
  `\appendixtables` needs to be added in front of appendix tables
  
  Please add `\clearpage` between each table and/or figure. Further guidelines on figures and tables can be found below.
output:
  rticles::copernicus_article: 
    highlight: NULL
    keep_tex: true
  bookdown::pdf_book:
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
---

# Introduction

general introduction on forest carbon accounting in Canada (1-2 paragraphs) and the concept of fire severity overall, and how these two relate. Managed vs unmanaged forest natural disturbance accounting in Canada, explain that part.

Wildfire is on par with insects as the largest stand-replacing disturbance process in Canada's forest, impacting \~1-3 Mha of Canada's 355 Mha forested area in a typical year [@hanes2019]. In Canada's reliable 40-year burned area record, six years have exceeded 4 Mha of burned area, largely in continental boreal and dry temperate forests west of the Great Lakes. Of this, managed forest accounts for xxx% of the area burned between 1980 and 2022; publicly-owned forest under long-term licence to private timber companies forms the vast majority of Canada's managed forest [@stinson2019], allowing for simplified and harmonized forest inventory and carbon modelling across jurisdictions (ref??). Burned area is dominated by a relatively small number of very large fires, with 3% of fires constituting 97% of the burned area [@stocks2002]. Lightning-caused fires account for approximately half of all ignitions and between xxx and xxxx% of burned area, but no distinction is made between human and lightning ignition for carbon accounting purposes. Annual burned area mapping at 30 metre resolution is conducted using a composite of satellite and aerial mapping; the relatively small number of large fires, and their slow vegetation regeneration [@white2017] allows for reliable mapping using multispectral imagery such as Landsat within the year of the fire [@whitman2018].

In CBM-CFS, spatially referenced stand lists representing large homogenous stands that fall within spatial units (ecozone-provincial intersections) are randomly (??) drawn, even when applying precisely mapped burned areas. In Canada's forests, a combination of disturbance history (), soils, and less frequently topographic variables determine leading tree species; at local scales (1-100 ha), tree species plays a major role in determining ecosystem susceptibility to fire [@bernier2016] where older, conifer-dominated forests burn at very high rates relative to adjacent deciduous or mixed stands. Even when deciduous and mixed forests do burn, they do so at consistently lower severity compared to all but the most xeric conifer forests [@whitman2018]. Currently, biomass consumption estimates are based on observed fire weather (and modelled using the Canadian Fire Behaviour Prediction Systems) at the time of satellite fire activity detection, but applied only at this spatially-referenced aggregated scale. Thus, important biases in fire activity towards older and moderate to poorly-drained forests are not resolved, and only a regionally-averaged fire severity is applied.

To support recent advances in operational burn severity mapping for Canada [@whitman2020] alongside multi-decade reliable burned area records that provide certainty on fire start and end dates [@hall2020] , the CBM DMs also need to be upgraded.

something about dynamic veg models like landis and how they represent fire disturbance -then how most MRV models and quickly how they do fire disturbance -even a bit on the GFED/GFAS world too

that ESSD frames it well, worth reading the intro part in detail) (recent Smyth and Campbell papers too) (other recent Canadian fire-carbon things, Walker - esp is supports consistent patterns in proportional carbon loss)

In this document, we outline the evidence-based fire Disturbance Matrices updated and designed for a spatially-explicit update to the CBM, anchored in a three severity class paradigm. These fire carbon flux models are built from a blend of aggregated field data linked to remotely sensed severity, as well as insights from fire physics and experimental fires. Key knowledge gaps are also highlighted, with interim solutions presented until further quantification can be done in field studies, such as from further wildfire observations, experimental fires, or prescribed fires.

# Methods

```{r loadLibsEtc, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(kableExtra)
library(tinytex)
library(formatR)
library(data.table)
library(directlabels)
library(ggrepel)
library(gtools)
library(rticles)
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE)

#original list
#ecozones.list <- list("AM","TP","TSW","BSW","BP","P","TC","BC","PM","MC","HP","TSE","BSE")

#complete list, ordered by decreasing CNFDB burned area:
#ecozones.list <- list("BSW","TP","TSW","BP","BC","BSE","TSE","MC","HP","TC","PM","SuP","SeP","AM","MP")

##working list as of 2023-04-13 that has all the data we need, no MP, no P
ecozones.list <- list("BSW","TP","TSW","BP","BC","BSE","TSE","MC","HP","TC","PM","AM")
```

## Biomass pools of the Generic Carbon Budget Model

Short section explaining the pool definitions most relevant to fire.

## Axioms of forest carbon budget after fire

To simplify the process of the creation of the DMs as a distillation of the complexities of fire severity and combustion patterns, the following logical axioms are proposed and maintained throughout:

1.  Disturbance matrices are to be in terms of mortality, not survival

2.  Crown Fraction Burned (CFB) is a mass-based estimate of the portion of foliage consumed in flaming, and is inclusive of merchantable and submerchantable trees, both broadleaf and needleleaf

3.  Snags are inclusive of both those killed by prior fire as well as those killed by all other causes

4.  In submerchantable trees, mortality = CFB

5.  In submerchantable trees, mortality is \<= 1

6.  In merchantable stands, CFB \< mortality

7.  Survival = 1 - mortality

8.  CFB \< survival

9.  The girdled fraction of trees = mortality - CFB

10. Survival \<= 1 and also \>= 0

Of these, Crown Fraction Burned (CFB) is both highly critical and a concept used primarily in fire behaviour science but not carbon accounting nor fire ecology. CFB was introduced in the 1992 Fire Behaviour Prediction System documentation, and provides a simple continuous 0-100 variable for only the consumption of foliage (inclusive of both conifer and broadleaf), as opposed to ordinal and less precise systems like Crown Fire Severity Index that allows the user to specify moreso which pools of canopy biomass are consumed, but not the degree to which a given pool is consumed.

## Ground plot and remotely sensed fire severity data

!!!Ellen to insert methods here - including the figure of where the samples are from etc.

## Combustion gas emission ratios

Certain variables, like the fractionation of CO2:CH4:CO, are constant throughout ecozones, but vary by flaming vs smouldering. They are defined in a global variables table:

```{r defineVars, echo=FALSE, message=FALSE, warning=FALSE}


#populate the values first:


####OPTION 1 (preferred)
#values directly from CFFEPS-FireWork
#Note that we are using the flaming CO2/CH4/CO from CBM originally, and smouldering from CFFEPS, the emissions module for ECCC's FireWork national smoke model (http://www.geosci-model-dev.net/12/3283/2019/). Specifically, we are using the arithmetic average of "smouldering" and "residual" phases.
##global.vars <- list(0.89, 0.004, 0.07, 0.79, 0.013, 0.16) ##Note: this is the stoichiometrically correct ratio, which includes non-CH4 hydrocarbons AND total PM, so CO2+CO+CH4 is only ~0.96


#### OPTION 1A (interim use March 2023)
#global.vars <- list(0.926, 0.004, 0.07, 0.827, 0.013, 0.16) ##Note: this retains the emissions ratios for CO2:CO:CH4 for the major gases, but excludes PM and non-CH$ hydrocarbons.  Just for interim use to evaluate the smouldering component.

#### OPTION 1B (interim use July 2023)

### Hayden et al showed that x% of total carbon goes into total PM (assume 51% carbon content for the time being), and x% of total PM goes into PM2.5, so the CFFEPS values in Option 1A, but minus the PM phase (which is accounted for below in their own fluxes)

##using Hayden et al as the example for smouldering BC emissions, and Permar 2021 from WE-CAN (https://doi.org/10.1029/2020JD033838) for flaming BC EF, otherwise, unchanged from Chen et al CFFEPS EFs as given, but using 51% carbon content of fuels


CarbonEFs <- read.csv("~/nrcan-cfs-fire/FireDMs/GMD/CarbonCalculator.csv")

CarbonEFs_pivot_wider <- CarbonEFs[,1:3] %>% pivot_wider(names_from = Phase, values_from = Value)

global.vars <- CarbonEFs$Value

#then label names using updated "atmosphere sink" pools as they say, which is to say, carbon-focused EFs as fraction of 
names(global.vars) <- array(as.character(CarbonEFs$VarName))


### convert to list for easier referencing later down
global.vars <- as.list(global.vars)

#DID NOT RUN:
#global.vars$FlamingCO2 #returns desired value as double



####OPTION 2 (simple)
#The provided 0.9,0.01,0.09 represents an MCE of 0.90 and therefore a mixed plume very similar to that from ARCTAS data by Simpson et al 2011 (10.5194/acp-11-6445-2011)
###global.vars <- list(0.9,0.01,0.09,0.9,0.01,0.09) ##using the same mixed plume from the current CBM, so flaming is the same as smouldering





#can add/subtract ecozones here as needed.  Note that Mixedwood Plains not included here (but could/should be)

##load Ellen's data (InterimValue==False)
VarDefs <- read.csv("~/nrcan-cfs-fire/FireDMs/FireDMTableDefs.csv")

VarDefs$SeverityClass <- factor(VarDefs$SeverityClass,levels = c("Low", "Mod", "High"))



```

```{r globalVarsEmissions, echo=FALSE, message=FALSE, warning=FALSE}
kbl(CarbonEFs_pivot_wider, caption = "Emissions factors in flaming and smouldering phase, expressed as portion of unburned biomass carbon content") %>%
  kable_minimal()  #%>%
          #kable_styling(latex_options = "scale_down") %>%
  #kable_styling(latex_options = "hold_position")
```

where CO~2~ is responsible for `r as.numeric(global.vars$FlamingCO2)*100`% of emissions in the flaming phase, but only `r as.numeric(global.vars$SmoulderingCO2)*100`% of emissions in the smouldering phase, with a doubling of CO emissions and tripling of CH~4~ emissions. With a Global Warming Potential of CO equal to 1.9 and CH~4~ of 25, the Global Warming Potential per unit of biomass consumption in the smouldering phase is `r round(((as.numeric(global.vars$SmoulderingCO2*1+global.vars$SmoulderingCH4*25+global.vars$SmoulderingCO*1.9))/(as.numeric(global.vars$FlamingCO2*1+global.vars$FlamingCH4*25+global.vars$FlamingCO*1.9))),2)` times higher in global warming potential compared to flaming, not including differential aerosol production and injection heights, however. Note that these proposed emissions factors for flaming vs smouldering are aligned with those currently used in Canada's operational wildfire smoke air quality model, FireWork [@chen2019]. With flaming and smouldering each contributing roughly equally to wildfire emissions, these distinct flaming and smouldering emissions rates correspond well with aircraft smoke chemistry observations by [@simpson2011] and [@hayden2022] and are themselves very similar to prior emissions factors used in CBM. Note that as current described, the sum of CO~2~, CH~4~, and CO emissions from wildfires only represent approximately 95% of the fire carbon mass emitted to the atmosphere, with 0.5-2.0% of biomass emitted as particulate matter (e.g. PM2.5, but also PM1 and PM10 classes of particulates at 1 and 10 um diameters, respectively), and an additional 3% [@hayden2022] to as little as 1% [@simon2010] composed of non-methane organic gases that have a large range in global warming potentials as compared to CH~4~.

## Litter layer area-wise consumption by severity class

The litter layer forms the first biomass pool in which a spreading fire consumes fuel. In low-severity fires, the litter layer may be consumed little to no underlying duff material consumed, nor any tree mortality [@hessburg2019]. Logically, since litter consumption is required for the ignition of the underlying duff layer, this litter area-wise fractional consumption also informs and constrains duff consumption.

```{r UnBurnedForestFloorByEcozone, echo=FALSE, message=FALSE, warning=FALSE}

##load Ellen's data (InterimValue==False)


#subset to just the variable of interest:



VarDefs.Unburned.Litter <- VarDefs[VarDefs$Variable.Name == "Unburned.litter.area",]



VarDefs.dt <- as.data.table(VarDefs.Unburned.Litter)

Unburned.Litter.wide <- dcast(VarDefs.dt,Ecozone~SeverityClass,value.var = "Value")

###then re-order the Ecozone factor (via https://stackoverflow.com/a/46130642)

Unburned.Litter.wide <- Unburned.Litter.wide[order(factor(Ecozone,levels = as.matrix(ecozones.list)))]

kbl(Unburned.Litter.wide, caption = "Unburned litter area by ecozone and severity class.  The majority of the data comes from studies in the Boreal Plains and Boreal Shield West, and so values are extrapolated from those two well-observed ecozones to all others.") %>%
  kable_minimal()#  %>%
          #kable_styling(latex_options = "scale_down") %>%
  #kable_styling(latex_options = "hold_position")
```

## Duff Consumption

While consumption of fine fuels in the litter layer of the forest floor is nearly complete for any given fire intensity, consumption of deeper organic soil horizons (F+H layers in upland forests and upper peat layers in wetlands) is more drought dependent. In this scheme, we utilize the Forest Floor Fuel Consumption (FFFC) model and data of [@degroot2009], modified to compute the relative amount of consumption (scalar from 0 to 1) rather than an absolute value in \unit{0.2\,kg\,m^{-2}}:

```{=tex}
\begin{equation}
logit \left( \frac{FFFC}{FFFL}\right) = DC^{0.33}(FFFL)^{-0.17}-4.85
\end{equation}
```
where DC is the Fire Weather Index Drought Code, and FFFL is the Forest Floor Fuel Load (with ecozone averages given in [@letang2012] or site-level data where observed). While ultimately this scheme can be used on individual fires with estimated or measured fuel loading and specific Drought Code values, for the purposes of this first assessment, an ecozone-averaged fuel load and decadal composites of Drought Code is used to provide representative values. Specifically, a median Drought Code of detected fire hotspots in Canada from 2003-2021 using the same data as the Canadian CFEEPS-FireWork wildfire air quality model of [@chen2019] is presented below, along with proportional consumption values of the forest floor by ecozone:

```{r computeDuffConsump, echo=FALSE, message=FALSE, warning=FALSE}


#load the raw de Groot forest floor data: 

FFFC_Data <- read.csv("~/nrcan-cfs-fire/FireDMs/FFFC_Data.csv")

##First, logit transform the data, then apply basically Kerry's model?

### for now, filter our values > 1

#FFFC_Data <- FFFC_Data %>% filter(Frac_load_consump < 1)

FFFC_Data$Frac_load_consump <- ifelse(FFFC_Data$Frac_load_consump>1,1,FFFC_Data$Frac_load_consump)

FFFC_Data$Frac_load_consump_logit <- logit(FFFC_Data$Frac_load_consump, min = 0.00001, max = 1.01)

##kerry's version of this data is 0.0168*DC^0.71*Load^0.671

#FFFC.Frac.Consume.nls <- nls(Frac_load_consump_logit ~ (DC^a)+(Load*b)+c,
#                 data = FFFC_Data,
#                 start = list(a = 0.71, b = 0.671,c=0),na.action=na.omit)
#summary(FFFC.Frac.Consume.nls)

FFFC.Frac.Consume.nls <- nls(Frac_load_consump_logit ~ (DC^a)*(Load^b)+c,
                 data = FFFC_Data,
                 start = list(a = 0.71, b = 0.671,c=0),na.action=na.omit)
summary(FFFC.Frac.Consume.nls)

### do a predict.nls (not run)

nls.pred <- inv.logit(predict(FFFC.Frac.Consume.nls,newdata=FFFC_Data))

FFFC_Data <- cbind(FFFC_Data,nls.pred)

ggplot(FFFC_Data, aes(Frac_load_consump,nls.pred)) + geom_point() + geom_abline(intercept = 0, slope = 1) + ylim(0,1) + geom_abline(intercept = 0, slope = 1.25) + geom_abline(intercept = 0, slope = 0.75)






#load an array of median DC values by ecozone (provided here hardcoded from Quinn Barber's dataframes of all Canadian hotspots from CWFIS 2002-2022), using the exact same order of ecozones above:
Ecozones.fffc <- c("AM","TP","TSW","BSW","BP","P","TC","BC","PM","MC","HP","TSE","BSE")
Median.DC <- c(270,369,297,239,242,242,254,250,268,452,204,98,123)
Litter.Load <- 0.25 #litter load as an average from Thompson et al 2017, across a range of boreal forest sites, doi: 10.1139/cjfr-2016-0475

# then the median forest floor load, minus an average litter value (provided here hardcoded from 10.1139/x2012-093):
Duff.Load <- c(10.9,15,1.7,8.8,9.8,9.8,8.31,8.31,15.2,6,7.9,1.7,10.9)

#Duff.consump.kg.m2 <- 0.016872*Median.DC^0.71*Duff.Load^0.671 - Litter.Load
Duff.consump.frac.logit <- Median.DC^0.33*Duff.Load^(-0.171)-4.8

Duff.consump.frac <- inv.logit(Duff.consump.frac.logit)

Duff.consump.kg.m2 <- Duff.consump.frac * Duff.Load

# start creating a single list object to encapsulate all the modelling:
#where FFFC is "Forest Floor Fuel Consumption" a la de Groot's naming convention:

FFFC <- as.data.frame(cbind(Ecozones.fffc,Median.DC,Duff.Load,round(Duff.consump.kg.m2,digits = 2),round(Duff.consump.frac,digits = 2)))
names(FFFC) <- c("Ecozone","Median.DC.of.burning","Median.Duff.Load.kg.m2","Duff.consump.kg.m2","Duff.consump.frac")

##re-order data.frame by ecozones.list order
FFFC <- arrange(FFFC,factor(Ecozone, levels = as.matrix(ecozones.list)))

## for example:
#FFFC$Ecozone.name[1]

### and to query values:
#FFFC$Duff.consump.frac[FFFC$Ecozone == "BP"]
```

```{r DuffConsumpTable, echo=FALSE, message=FALSE, warning=FALSE }
kbl(FFFC, caption = "Fire Weather, fuel loading, and duff consumption values per ecozone") %>%
  kable_minimal()  #%>%
          #kable_styling(latex_options = "scale_down") %>%
  #kable_styling(latex_options = "hold_position")
```

Note that the maximum upland Forest Floor Fuel Load is approximately 30 kg m-2 [@letang2012]; higher values are typically seen only in peat ecosystems, where the above Forest Floor Fuel Consumption scheme does not apply. For Canadian peatlands, the CaMP model [@bona2020] is instead used in CBM. Within CaMP, a separate peatland water model driven by Drought Code determines the thickness of the unsaturated peat layer, and an amount approximating 12% of the thickness of the unsaturated peat is consumed as smouldering consumption. The peat-specific carbon pools and fire Disturbance Matrices are fully described in [@bona2020]; large peatland trees will still utilize the DM scheme described below.

Little data is available on the fraction of woody debris consumption alongside fire severity measurements. Coarse woody debris of overstory stems that makes up 60-80% of woody debris biomass in Canada's boreal and temperate forests [@hanes2021], with its moisture and consumption patterns largely follows the moisture regime of the Drought Code [@mcalpine1995]. In this modelling framework, the proportion of coarse (\>7.5 cm diameter) and medium (\>0.5 cm and \<7.5 cm) woody debris consumption is estimated based on detailed measurements of consumption from experimental fires. Coarse Woody Debris is responsible for approximately 50-75% of the total woody debris load in most ecozones, and approximately 60% of the total woody debris consumption. Ecozone-level CWD consumption rates are summarized as:

```{r CWDByEcozone, echo=FALSE, message=FALSE, warning=FALSE}

#subset to just the variables of interest:

VarDefs.CWD <- VarDefs[VarDefs$Variable.Name == "MedDOM.Comb.Frac",]

VarDefs.dt <- as.data.table(VarDefs.CWD)

CWD.wide <- dcast(VarDefs.dt,Ecozone~SeverityClass,value.var = "Value")

CWD.wide <- CWD.wide[order(factor(Ecozone,levels = as.matrix(ecozones.list)))]

kbl(CWD.wide, caption = "Coarse Woody debris consumption rates from pre/post measurements in experimental fires") %>%
  kable_minimal()#  %>%
          #kable_styling(latex_options = "scale_down") %>%
  #kable_styling(latex_options = "hold_position")
```

Note that where historical burn severity data is not available, and instead the fire classification type of surface, intermittent crowning, and active crown fire are used as proxies for low, moderate, and high severity fire, respectively. Fine woody debris \<0.5 cm in diameter is consumed at the exact same rate as the litter pool (see section above).

## Drivers of C losses in the tree canopy

### Overstory tree mortality and consumption

Numerous process-driven [@michaletz2006] or empirical [@hood2017] tree mortality models are present and show significant skill in predicting tree mortality based on fire behaviour (i.e. flame length, rate of spread). Since the driving data in this model is satellite-derived fire severity over the landscape scale, fire behaviour metrics such as flame length or scorching height of bark are not available as a continuous mapped product. Instead, softwood and hardwood overstory mortality is calculated per ecozone as a function of satellite-observed fire severity using aggregated ground plot data:

```{r MortByEcozone, echo=FALSE, message=FALSE, warning=FALSE}

#subset to just the variable of interest:
VarDefs.SW.Mort <- VarDefs[VarDefs$Variable.Name == "SW.Mort",]

VarDefs.dt <- as.data.table(VarDefs.SW.Mort)

SW.Mort.wide <- dcast(VarDefs.dt,Ecozone~SeverityClass,value.var = "Value")

SW.Mort.wide <- SW.Mort.wide[order(factor(Ecozone,levels = as.matrix(ecozones.list)))]

kbl(SW.Mort.wide, caption = "Softwood fractional mortality by ecozone, as dervied from median values from field studies") %>%
  kable_minimal()#  %>%
          #kable_styling(latex_options = "scale_down") %>%
  #kable_styling(latex_options = "hold_position")
```

And since large-diameter, live trees killed by fire do not experience significant live stemwood consumption, the entirity of the live stemwood biomass pool that is killed is transferred to the snag pool. Note that the field data and disturbance modelling undertaken here only accounts for tree mortality within the calender year of the fire, and delayed mortality of over one year has been documented in boreal low and moderate severity fires [@angers2011]where less than half of total mortality occurs after the year of the fire. Thus, the modelling here does not account for delayed mortality that may extend upwards of 5 years after fire.

Crown Fraction Burned (CFB) speaks to the fraction of the live canopy that is itself consumed in the flaming front. The alternate outcomes being survival of the foliage, or the mortality of the tree without canopy consumption, resulting in the dropping of foliage onto the forest floor. From the axioms stated earlier, the CFB must be lower than or equal to the mortality rate, using field studies that show any partial crown consumption is likely sufficient to result in high rates if not complete mortality [@hood2017], which is the case in Canada's trees with primarily thin bark. From field studies, the following ecozone-specific CFB values are found:

```{r CFBByEcozone, echo=FALSE, message=FALSE, warning=FALSE}

#subset to just the variable of interest:
VarDefs.SW.CFB <- VarDefs[VarDefs$Variable.Name == "SW.CFB",]

VarDefs.dt.SW.CFB <- as.data.table(VarDefs.SW.CFB)

SW.CFB.wide <- dcast(VarDefs.dt.SW.CFB,Ecozone~SeverityClass,value.var = "Value")

SW.CFB.wide <- SW.CFB.wide[order(factor(Ecozone,levels = as.matrix(ecozones.list)))]

kbl(SW.CFB.wide, caption = "Softwood crown fraction burned by ecozone, as dervied from median values from field studies") %>%
  kable_minimal()#  %>%
          #kable_styling(latex_options = "scale_down") %>%
  #kable_styling(latex_options = "hold_position")
```

The consumption of live bark biomass is a pool in the model, and consumption rates can be defined by severity class. At the moment, lacking robust field data on bark biomass consumption rates across ecozones and severity classes (which are a small portion of the overall biomass), the bark proportional consumption rate is set to 34% of the overstory mortality rate, based only on a single well-observed high severity fire in Taiga Plains by Santin 2015.

A major distinction is made between softwood and hardwood trees, where in Canada's boreal forests, a large fraction of hardwood trees (see Appendix E) are able to resprout even when the main stem has been killed by an intense forest fire [@brown1987]. Accordingly, the root mortality rates differ greatly between softwoods and hardwoods, with softwood root mortality equal precisely to stem mortality, while in resprouting hardwoods, little root mortality is observed even after intense fire [@pérez-izquierdo2019]. Though GCBM can resolve a species list down to the pixel level, currently an ecozone-level regional average composition of hardwood species with resprouting traits is used and is shown below:

```{r ReSproutByEcozone, echo=FALSE, message=FALSE, warning=FALSE}

#subset to just the variable of interest:
VarDefs.HW.ReSprout <- VarDefs[VarDefs$Variable.Name == "HW.ReSprout",]

VarDefs.dt.HW.ReSprout <- as.data.table(VarDefs.HW.ReSprout)

SW.CFB.wide <- dcast(VarDefs.dt.SW.CFB,Ecozone~SeverityClass,value.var = "Value")

SW.CFB.wide <- SW.CFB.wide[order(factor(Ecozone,levels = as.matrix(ecozones.list)))]

kbl(SW.CFB.wide, caption = "Softwood crown fraction burned by ecozone, as dervied from median values from field studies") %>%
  kable_minimal()#  %>%
          #kable_styling(latex_options = "scale_down") %>%
  #kable_styling(latex_options = "hold_position")
```

Concurrently, the fraction of fine roots contained within the combustible forest floor layers can be a close to or exceeding 50% of the fine root biomass [@strong1985], and burns alongside the organic soils [@benscoter2011]. As a result, the calulation for softwood fine root consumption and mortality are as follows, using Softwood as an example:

```{=tex}
\begin{equation}
SWFineRootConsump = SW.Mort \times SW.Prop.Fine.Root.duff \times Duff.Consump.Fract
\end{equation}
```
```{=tex}
\begin{equation}
SWFineRootMort.AG = SW.Mort \times SW.Prop.Fine.Root.duff \times (1-Duff.Consump.Fract) \times (1-ReSproutFactor)
SWFineRootMort.BG = SW.Mort \times (1-SW.Prop.Fine.Root.duff)
\end{equation}
```
In contrast, the larger diameter of the coarse root biomass pool prevents its consumption during any smouldering of the duff layer, and the mortality rate of coarse roots is simply proportional to that of the stemwood overall.

### Understory tree mortality and consumption

Understory (or small diameter overstory) tree mortality is defined seperately in the model, but given the lack of data on diameter classes in the severity data, robust field data on differing mortality rates of smaller diameter trees is not available, and so the understory tree mortality rate is set equal to the overstory rate as defined in the table above. Note that trees with a top height less than 1.4 m are not considered in this pool, and instead are lumped into the "other" pool.

### Snag and stump consumption

Compared to live stemwood of the same diameter, the low moisture content of standing dead stemwood (snags) allows for much greater consumption during the passage of an intense flaming front. The snag branch pool experiences almost complete combustion, while the largest biomass pool of the main standing dead stemwood <!-- !!(see doi:10.1002/ecs2.2744). There is also a more physics-bsaed argument around a reasonable diameter reduction amount, and mean dbh by ecozone!!. -->

## Construction fire disturbance matrices

Give total number of global parameters, and parameters per ecozone, and then total parameters, and what % of total parameters we have so far filled with data

```{r loadVarDefsSourceSink, echo=FALSE,message=FALSE, warning=FALSE}

#list of ecozone-specific terms (with and without severity dependence)
#first, import blank template that works for a single ecozone:
#VarDefs.generic <- as.data.frame(read.csv("~/nrcan-cfs-fire/FireDMs/VarDefsGeneric.csv"))
#VarDefs.generic <- VarDefs.generic[,1:7]

#then, replicate for each severity level*ecozone

#use slice from dplyr and each to replicate the template for each ecozone
#VarDefs <- VarDefs.generic %>% slice(rep(1:n(), each = length(ecozones.list)))

#fill in ecozone names:
#VarDefs$Ecozone <- rep(as.matrix(ecozones.list),times = nrow(VarDefs.generic))

#Once this is done and filled in with data from observations, load the canonical version: 
# this will overwrite the above loop
#NOT RUN (YET)
#VarDefs <- read.csv("~/nrcan-cfs-fire/FireDMs/FireDMTableDefs.csv")




#sink-source DM list:
#first, import blank template that works for a single ecozone:
SourceSinkGeneric <- read.csv("~/nrcan-cfs-fire/FireDMs/SourceSinkGeneric.csv")


#then, replicate for each severity level*ecozone
SourceSink <- SourceSinkGeneric %>% slice(rep(1:n(), each = length(ecozones.list)))

#fill in ecozone names:
SourceSink$Ecozone <- rep(as.matrix(ecozones.list),times = nrow(SourceSinkGeneric))


#Once this is done and filled, load the canonical version: 
# this will overwrite the above loop
#NOT RUN (YET)
#SourceSink <- read.csv("~/FireDMs/SourceSinkLong.csv")


```

# Results and example applications

```{r DefineDMvalues, echo=FALSE,message=FALSE, warning=FALSE}

j <- 1

for (j in seq(1:length(ecozones.list))) {

  ecozone <- as.character(ecozones.list[j]) #run this loop once for every ecozone

  #print(j)

    
#FluxID: 1
#Source: Softwood (SW) Merch 
#sink: SW Merch
#Plain Language Summary of flux: survival of conifers
#Pseudocode: survival = 1-mortality
#Notes:  by axiom, survival = 1-mortality,

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 1 & SourceSink$SeverityClass == "Low"] <- 1 - (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 1 & SourceSink$SeverityClass == "Mod"] <- 1 - (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 1 & SourceSink$SeverityClass == "High"] <- 1 - (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])

#but, I'm not doing this easily across all three severity classes, no need to run it across each severity class as its own line....

#FluxID: 2
#Source: SW Merch 
#sink: SW Stem Snag
#PLS: Mortality rate of large conifers (includes those with and without burned foliage)
#Pseudocode: as provided from field data, f(ecozone, severity class)
#Notes: mortality >= CFB; may not be the case in extremely fire-tolerant stands, but valid the vast majority of the time
#Notes2: just pulling Softwood CFB 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 2 & SourceSink$SeverityClass == "Low"] <- (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 2 & SourceSink$SeverityClass == "Mod"] <- (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 2 & SourceSink$SeverityClass == "High"] <- (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])



#FluxID: 3
#Source: SW Merch 
#sink: Black Carbon
#PLS: live stemwood to black carbon
#Pseudocode: =0, since no live stemwood -> 0 BC
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 3 & SourceSink$SeverityClass == "Low"] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 3 & SourceSink$SeverityClass == "Mod"] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 3 & SourceSink$SeverityClass == "High"] <- 0


#FluxID: 5
#Source: SW Foliage
#sink: Above Ground Very Fast DOM
#PLS: Post-fire litterfall (heat-killed but not burned, then falls to ground within the season)
#Pseudocode: Remainder of all fluxes above.
#Notes: assume 100% of heat-killed litter falls within the year of fire

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 5 & SourceSink$SeverityClass == "Low"] <- VarDefs$Value[VarDefs$Variable.Name == 'SW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'] - VarDefs$Value[VarDefs$Variable.Name == 'SW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']
  
SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 5 & SourceSink$SeverityClass == "Mod"] <- VarDefs$Value[VarDefs$Variable.Name == 'SW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'] - VarDefs$Value[VarDefs$Variable.Name == 'SW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 5 & SourceSink$SeverityClass == "High"] <- VarDefs$Value[VarDefs$Variable.Name == 'SW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'] - VarDefs$Value[VarDefs$Variable.Name == 'SW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']


#FluxID: 6
#Source: SW Foliage
#sink: CO2
#PLS: CO2 emission from Crown Fraction Burned
#Pseudocode: CFB*FlamingCO2
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 6 & SourceSink$SeverityClass == "Low"] <- global.vars$FlamingCO2 *  VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 6 & SourceSink$SeverityClass == "Mod"] <- global.vars$FlamingCO2 *  VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 6 & SourceSink$SeverityClass == "High"] <- global.vars$FlamingCO2 *  VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]

#FluxID: 7
#Source: SW Foliage
#sink: CH4
#PLS: CH4 emission from Crown Fraction Burned
#Pseudocode: CFB*FlamingCH4
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 7 & SourceSink$SeverityClass == "Low"] <- global.vars$FlamingCH4 *  VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 7 & SourceSink$SeverityClass == "Mod"] <- global.vars$FlamingCH4 *  VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 7 & SourceSink$SeverityClass == "High"] <- global.vars$FlamingCH4 *  VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]

#FluxID: 8
#Source: SW Foliage
#sink: CO
#PLS: CO emission from Crown Fraction Burned
#Pseudocode: CFB*FlamingCO
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 8 & SourceSink$SeverityClass == "Low"] <- global.vars$FlamingCO *  VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 8 & SourceSink$SeverityClass == "Mod"] <- global.vars$FlamingCO *  VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 8 & SourceSink$SeverityClass == "High"] <- global.vars$FlamingCO *  VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]






#FluxID: 10
#Source: SW Other
#sink: SW Branch Snag
#PLS: Portion of "other" pool as killed by fire but otherwise unconsumed branches
#Pseudocode: (CFB * (1-SW.LgBranch.Comb.Frac))*SW.BW.frac.of.other

#Notes:  #since 1-SW.LgBranch.Comb.Frac is the snag creation rate

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "Low"] <- (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"] *
(1 - VarDefs$Value[VarDefs$Variable.Name == "SW.LgBranch.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])) * VarDefs$Value[VarDefs$Variable.Name == "SW.BW.frac.of.other" & VarDefs$Ecozone == ecozone]            

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "Mod"] <- (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"] *
(1 - VarDefs$Value[VarDefs$Variable.Name == "SW.LgBranch.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])) * VarDefs$Value[VarDefs$Variable.Name == "SW.BW.frac.of.other" & VarDefs$Ecozone == ecozone]  

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "High"] <- (VarDefs$Value[VarDefs$Variable.Name == "SW.CFB" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"] *
(1 - VarDefs$Value[VarDefs$Variable.Name == "SW.LgBranch.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])) * VarDefs$Value[VarDefs$Variable.Name == "SW.BW.frac.of.other" & VarDefs$Ecozone == ecozone]   
                                                                                                                      
#FluxID: 11
#Source: SW Other
#sink: CO2
#PLS: Proportional Combustion sum of branches, stumps, small trees and bark (mix of flaming and smouldering)
#Pseudocode:   (Flux10*FlamingCO2)+
# (Stumps.frac.of.other*DOM.Comb.Rate*SmoulderingCO2)+
# (Litter.frac.burned*SmTree.frac.other*FlamingCO2)+
# (Bark.frac.other*Bark.Comb.Frac*FlamingCO2)

#Notes:  works so far and gives reasonable values of ~0.17, 0.19, 0.2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 11 & SourceSink$SeverityClass == "Low"] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "Low"] * global.vars$FlamingCO2 +  
VarDefs$Value[VarDefs$Variable.Name == "SW.stumps.frac.of.other" & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO2 + (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]*VarDefs$Value[VarDefs$Variable.Name == "SW.SmTree.frac.of.other" & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO2) + (VarDefs$Value[VarDefs$Variable.Name == "SW.bark.frac.of.other" & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == "Bark.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"] * global.vars$FlamingCO2)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 11 & SourceSink$SeverityClass == "Mod"] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "Mod"] * global.vars$FlamingCO2 +  
VarDefs$Value[VarDefs$Variable.Name == "SW.stumps.frac.of.other" & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO2 + (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]*VarDefs$Value[VarDefs$Variable.Name == "SW.SmTree.frac.of.other" & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO2) + (VarDefs$Value[VarDefs$Variable.Name == "SW.bark.frac.of.other" & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == "Bark.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"] * global.vars$FlamingCO2)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 11 & SourceSink$SeverityClass == "High"] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "High"] * global.vars$FlamingCO2 +  
VarDefs$Value[VarDefs$Variable.Name == "SW.stumps.frac.of.other" & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO2 + (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]*VarDefs$Value[VarDefs$Variable.Name == "SW.SmTree.frac.of.other" & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO2) + (VarDefs$Value[VarDefs$Variable.Name == "SW.bark.frac.of.other" & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == "Bark.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"] * global.vars$FlamingCO2)

#FluxID: 12
#Source: SW Other
#sink: CH4
#PLS: Proportional Combustion sum of branches, stumps, small trees and bark (mix of flaming and smouldering)
#Pseudocode:   (Flux10*FlamingCH4)+
# (Stumps.frac.of.other*DOM.Comb.Rate*SmoulderingCH4)+
# (Litter.frac.burned*SmTree.frac.other*FlamingCH4)+
# (Bark.frac.other*Bark.Comb.Frac*FlamingCH4)

#Notes:  works so far and gives reasonable values of ~0.017, 0.019, 0.02

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 12 & SourceSink$SeverityClass == "Low"] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "Low"] * global.vars$FlamingCH4 +  
VarDefs$Value[VarDefs$Variable.Name == "SW.stumps.frac.of.other" & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCH4 + (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]*VarDefs$Value[VarDefs$Variable.Name == "SW.SmTree.frac.of.other" & VarDefs$Ecozone == ecozone]*global.vars$FlamingCH4) + (VarDefs$Value[VarDefs$Variable.Name == "SW.bark.frac.of.other" & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == "Bark.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"] * global.vars$FlamingCH4)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 12 & SourceSink$SeverityClass == "Mod"] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "Mod"] * global.vars$FlamingCH4 +  
VarDefs$Value[VarDefs$Variable.Name == "SW.stumps.frac.of.other" & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCH4 + (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]*VarDefs$Value[VarDefs$Variable.Name == "SW.SmTree.frac.of.other" & VarDefs$Ecozone == ecozone]*global.vars$FlamingCH4) + (VarDefs$Value[VarDefs$Variable.Name == "SW.bark.frac.of.other" & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == "Bark.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"] * global.vars$FlamingCH4)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 12 & SourceSink$SeverityClass == "High"] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "High"] * global.vars$FlamingCH4 +  
VarDefs$Value[VarDefs$Variable.Name == "SW.stumps.frac.of.other" & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCH4 + (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]*VarDefs$Value[VarDefs$Variable.Name == "SW.SmTree.frac.of.other" & VarDefs$Ecozone == ecozone]*global.vars$FlamingCH4) + (VarDefs$Value[VarDefs$Variable.Name == "SW.bark.frac.of.other" & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == "Bark.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"] * global.vars$FlamingCH4)

#FluxID: 13
#Source: SW Other
#sink: CO
#PLS: Proportional Combustion sum of branches, stumps, small trees and bark (mix of flaming and smouldering)
#Pseudocode:   (Flux10*FlamingCO)+
# (Stumps.frac.of.other*DOM.Comb.Rate*SmoulderingCO)+
# (Litter.frac.burned*SmTree.frac.other*FlamingCO)+
# (Bark.frac.other*Bark.Comb.Frac*FlamingCO)

#Notes:  works so far 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 13 & SourceSink$SeverityClass == "Low"] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "Low"] * global.vars$FlamingCO +  
VarDefs$Value[VarDefs$Variable.Name == "SW.stumps.frac.of.other" & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO + (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]*VarDefs$Value[VarDefs$Variable.Name == "SW.SmTree.frac.of.other" & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO) + (VarDefs$Value[VarDefs$Variable.Name == "SW.bark.frac.of.other" & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == "Bark.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"] * global.vars$FlamingCO)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 13 & SourceSink$SeverityClass == "Mod"] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "Mod"] * global.vars$FlamingCO +  
VarDefs$Value[VarDefs$Variable.Name == "SW.stumps.frac.of.other" & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO + (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]*VarDefs$Value[VarDefs$Variable.Name == "SW.SmTree.frac.of.other" & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO) + (VarDefs$Value[VarDefs$Variable.Name == "SW.bark.frac.of.other" & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == "Bark.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"] * global.vars$FlamingCO)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 13 & SourceSink$SeverityClass == "High"] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 10 & SourceSink$SeverityClass == "High"] * global.vars$FlamingCO +  
VarDefs$Value[VarDefs$Variable.Name == "SW.stumps.frac.of.other" & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO + (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]*VarDefs$Value[VarDefs$Variable.Name == "SW.SmTree.frac.of.other" & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO) + (VarDefs$Value[VarDefs$Variable.Name == "SW.bark.frac.of.other" & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == "Bark.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"] * global.vars$FlamingCO)



#FluxID: 14
#Source: SW SubMerch
#sink: SW SubMerch
#PLS: Understory conifer survival rate
#Pseudocode:  =1-(mortality of submerch conifers in severity class) 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 14 & SourceSink$SeverityClass == "Low"] <- 1 - VarDefs$Value[VarDefs$Variable.Name == "SW.SubMerch.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 14 & SourceSink$SeverityClass == "Mod"] <- 1 - VarDefs$Value[VarDefs$Variable.Name == "SW.SubMerch.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 14 & SourceSink$SeverityClass == "High"] <- 1 - VarDefs$Value[VarDefs$Variable.Name == "SW.SubMerch.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]


#FluxID: 15
#Source: SW SubMerch
#sink: SW Branch Snag
#PLS: Understory conifer stems killed but not consumed
#Pseudocode:  = SubMerch mortality, since live understory trees don't get consumed in the fire, 

#notes: submerch trees assumed to not have large enough branches to avoid consumption in fire.  Equal to 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 15 & SourceSink$SeverityClass == "Low"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.SubMerch.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 15 & SourceSink$SeverityClass == "Mod"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.SubMerch.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 15 & SourceSink$SeverityClass == "High"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.SubMerch.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]


#FluxID: 16
#Source: SW SubMerch
#sink: CO2
#PLS: Understory Conifer consumption rate
#Pseudocode:  = 0 !IF! this is only about submerch stems 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 16 & SourceSink$SeverityClass == "Low"] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 16 & SourceSink$SeverityClass == "Mod"] <-0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 16 & SourceSink$SeverityClass == "High"] <- 0

#FluxID: 17
#Source: SW SubMerch
#sink: CH4
#PLS: Understory Conifer consumption rate
#Pseudocode:  = 0 !IF! this is only about submerch stems 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 17 & SourceSink$SeverityClass == "Low"] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 17 & SourceSink$SeverityClass == "Mod"] <-0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 17 & SourceSink$SeverityClass == "High"] <- 0


#FluxID: 18
#Source: SW SubMerch
#sink: CO
#PLS: Understory Conifer consumption rate
#Pseudocode:  = 0 !IF! this is only about submerch stems 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 18 & SourceSink$SeverityClass == "Low"] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 18 & SourceSink$SeverityClass == "Mod"] <-0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 18 & SourceSink$SeverityClass == "High"] <- 0

#FluxID: 19
#Source: SW Coarse roots
#sink: SW Coarse roots
#PLS: Surviving coarse roots in conifers
#Pseudocode:  =1-(conifer mortality rate)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 19 & SourceSink$SeverityClass == "Low"] <- 1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 19 & SourceSink$SeverityClass == "Mod"] <- 1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 19 & SourceSink$SeverityClass == "High"] <- 1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]

#FluxID: 20
#Source: SW Coarse roots
#sink: Above Ground Fast DOM
#PLS: Coarse Roots killed in fire but not combusted in organic soil
#Pseudocode:  =(conifer mortality rate)*(conifer coarse root fraction in organic soil)
#Note: assuming even if duff burns, coarse live roots don't burn alongsides SW.prop.Coarse.Root.duff

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 20 & SourceSink$SeverityClass == "Low"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"] * VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Coarse.Root.duff" & VarDefs$Ecozone == ecozone]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 20 & SourceSink$SeverityClass == "Mod"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"] * VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Coarse.Root.duff" & VarDefs$Ecozone == ecozone]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 20 & SourceSink$SeverityClass == "High"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"] * VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Coarse.Root.duff" & VarDefs$Ecozone == ecozone]


#FluxID: 21
#Source: SW Coarse roots
#sink: Below Ground Fast DOM
#PLS: Coarse Roots killed in fire but not combusted since they are in mineral soil
#Pseudocode:  =(conifer mortality rate)*(conifer coarse root fraction in mineral soil)
#Note: assuming even if duff burns, coarse live roots don't burn alongsides SW.prop.Coarse.Root.duff

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 21 & SourceSink$SeverityClass == "Low"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"] * (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Coarse.Root.duff" & VarDefs$Ecozone == ecozone])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 21 & SourceSink$SeverityClass == "Mod"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"] * (1 -  VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Coarse.Root.duff" & VarDefs$Ecozone == ecozone])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 21 & SourceSink$SeverityClass == "High"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"] * (1 -  VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Coarse.Root.duff" & VarDefs$Ecozone == ecozone])



#FluxID: 23
#Source: SW fine roots
#sink: Above Ground Very Fast DOM
#PLS: Fine roots killed but not burned in organic soil
#Pseudocode:  =(conifer mortality rate)*(fine root fraction in organic soil)*(1-fraction of duff consumed)
#notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 23 & SourceSink$SeverityClass == "Low"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"] * VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(1 - as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]))

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 23 & SourceSink$SeverityClass == "Mod"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"] * VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(1 - as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]))

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 23 & SourceSink$SeverityClass == "High"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"] * VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(1 - as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]))


#FluxID: 24
#Source: SW fine roots
#sink: Below Ground Very Fast DOM
#PLS: Fine roots killed but not burned in mineral soil
#Pseudocode:  =(conifer mortality rate)*(fine root fraction in mineral soil)
#notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 24 & SourceSink$SeverityClass == "Low"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"] * (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 24 & SourceSink$SeverityClass == "Mod"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"] * (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 24 & SourceSink$SeverityClass == "High"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"] * (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone])




#FluxID: 25
#Source: SW fine roots
#sink: CO2
#PLS: Fine roots combusted in duff
#Pseudocode:  =(conifer mortality rate)*(fine root fraction in organic soil)*(fraction of duff consumed)
#notes: since this is solely based on FFFC fraction, which isn't itself severity driven, there's no severity gradient in here.  Note also no relation to SW mortality (since you can burn off roots and not actually kill the tree, to a point)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 25 & SourceSink$SeverityClass == "Low"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 25 & SourceSink$SeverityClass == "Mod"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 25 & SourceSink$SeverityClass == "High"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO2


#FluxID: 26
#Source: SW fine roots
#sink: CH4
#PLS: Fine roots combusted in duff
#Pseudocode:  =(conifer mortality rate)*(fine root fraction in organic soil)*(1-fraction of duff consumed)
#notes: since this is solely based on FFFC fraction, which isn't itself severity driven, there's no severity gradient in here.  Note also no relation to SW mortality (since you can burn off roots and not actually kill the tree, to a point)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 26 & SourceSink$SeverityClass == "Low"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 26 & SourceSink$SeverityClass == "Mod"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 26 & SourceSink$SeverityClass == "High"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCH4



#FluxID: 27
#Source: SW fine roots
#sink: CO
#PLS: Fine roots combusted in duff
#Pseudocode:  =(conifer mortality rate)*(fine root fraction in organic soil)*(1-fraction of duff consumed)
#notes: since this is solely based on FFFC fraction, which isn't itself severity driven, there's no severity gradient in here.  Note also no relation to SW mortality (since you can burn off roots and not actually kill the tree, to a point)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 27 & SourceSink$SeverityClass == "Low"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 27 & SourceSink$SeverityClass == "Mod"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 27 & SourceSink$SeverityClass == "High"] <- VarDefs$Value[VarDefs$Variable.Name == "SW.prop.Fine.Root.duff" & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO





#Fluxes 28:54 Hardwoods
### HARDWOODS!!!!
###


#FluxID: 28
#Source: HW Merch 
#sink: HW Merch
#Plain Language Summary of flux: survival of conifers
#Pseudocode: survival = 1-mortality
#Notes:  by axiom, survival = 1-mortality,

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 28 & SourceSink$SeverityClass == "Low"] <- 1 - (VarDefs$Value[VarDefs$Variable.Name == "HW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 28 & SourceSink$SeverityClass == "Mod"] <- 1 - (VarDefs$Value[VarDefs$Variable.Name == "HW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 28 & SourceSink$SeverityClass == "High"] <- 1 - (VarDefs$Value[VarDefs$Variable.Name == "HW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])



#FluxID: 29
#Source: HW Merch 
#sink: HW Stem Snag
#PLS: Mortality rate of large broadleaf (includes those with and without burned foliage)
#Pseudocode: as provided from field data, f(ecozone, severity class)
#Notes: mortality >= CFB; may not be the case in extremely fire-tolerant stands, but valid the vast majority of the time
#Notes2: just pulling Softwood Mortality from field data

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 29 & SourceSink$SeverityClass == "Low"] <- (VarDefs$Value[VarDefs$Variable.Name == "HW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 29 & SourceSink$SeverityClass == "Mod"] <- (VarDefs$Value[VarDefs$Variable.Name == "HW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 29 & SourceSink$SeverityClass == "High"] <- (VarDefs$Value[VarDefs$Variable.Name == "HW.Mort" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])

#FluxID: 30
#Source: HW Merch 
#sink: Black Carbon
#PLS: live stemwood to black carbon
#Pseudocode: =0, since no live stemwood -> 0 BC
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 30 & SourceSink$SeverityClass == 'Low'] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 30 & SourceSink$SeverityClass == 'Mod'] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 30 & SourceSink$SeverityClass == 'High'] <- 0


#FluxID: 32
#Source: HW Foliage
#sink: Above Ground Very Fast DOM
#PLS: Post-fire litterfall (heat-killed but not burned, then falls to ground within the season)
#Pseudocode: Mortality-CFB
#Notes: assume 100% of heat-killed litter falls within the year of fire

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 32 & SourceSink$SeverityClass == 'Low'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'] - VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 32 & SourceSink$SeverityClass == 'Mod'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'] - VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 32 & SourceSink$SeverityClass == 'High'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'] - VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']

#FluxID: 33
#Source: HW Foliage
#sink: CO2
#PLS: CO2 emission from Crown Fraction Burned
#Pseudocode: CFB*FlamingCO2
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 33 & SourceSink$SeverityClass == 'Low'] <- global.vars$FlamingCO2 *  VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 33 & SourceSink$SeverityClass == 'Mod'] <- global.vars$FlamingCO2 *  VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 33 & SourceSink$SeverityClass == 'High'] <- global.vars$FlamingCO2 *  VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']

#FluxID: 34
#Source: HW Foliage
#sink: CH4
#PLS: CH4 emission from Crown Fraction Burned
#Pseudocode: CFB*FlamingCH4
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 34 & SourceSink$SeverityClass == 'Low'] <- global.vars$FlamingCH4 *  VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 34 & SourceSink$SeverityClass == 'Mod'] <- global.vars$FlamingCH4 *  VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 34 & SourceSink$SeverityClass == 'High'] <- global.vars$FlamingCH4 *  VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']

#FluxID: 35
#Source: HW Foliage
#sink: CO
#PLS: CO emission from Crown Fraction Burned
#Pseudocode: CFB*FlamingCO
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 35 & SourceSink$SeverityClass == 'Low'] <- global.vars$FlamingCO *  VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 35 & SourceSink$SeverityClass == 'Mod'] <- global.vars$FlamingCO *  VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 35 & SourceSink$SeverityClass == 'High'] <- global.vars$FlamingCO *  VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']

#FluxID: 37
#Source: HW Other
#sink: HW Branch Snag
#PLS: Portion of 'other' pool as killed by fire but otherwise unconsumed branches
#Pseudocode: (CFB * (1-HW.LgBranch.Comb.Frac))*HW.BW.frac.of.other

#Notes:  #since 1-HW.LgBranch.Comb.Frac is the snag creation rate

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'Low'] <- (VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'] * (1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.LgBranch.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'])) * VarDefs$Value[VarDefs$Variable.Name == 'HW.BW.frac.of.other' & VarDefs$Ecozone == ecozone]            

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'Mod'] <- (VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'] * (1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.LgBranch.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'])) * VarDefs$Value[VarDefs$Variable.Name == 'HW.BW.frac.of.other' & VarDefs$Ecozone == ecozone]  

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'High'] <- (VarDefs$Value[VarDefs$Variable.Name == 'HW.CFB' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'] * (1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.LgBranch.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'])) * VarDefs$Value[VarDefs$Variable.Name == 'HW.BW.frac.of.other' & VarDefs$Ecozone == ecozone]   

#FluxID: 38
#Source: HW Other
#sink: CO2
#PLS: Proportional Combustion sum of branches, stumps, small trees and bark (mix of flaming and smouldering)
#Pseudocode:   (Flux10*FlamingCO2)+
# (Stumps.frac.of.other*DOM.Comb.Rate*SmoulderingCO2)+
# (Litter.frac.burned*SmTree.frac.other*FlamingCO2)+
# (Bark.frac.other*Bark.Comb.Frac*FlamingCO2)

#Notes:  works so far and gives reasonable values of ~0.17, 0.19, 0.2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 38 & SourceSink$SeverityClass == 'Low'] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'Low'] * global.vars$FlamingCO2 +  
  VarDefs$Value[VarDefs$Variable.Name == 'HW.stumps.frac.of.other' & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO2 + (VarDefs$Value[VarDefs$Variable.Name == 'Unburned.litter.area' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']*VarDefs$Value[VarDefs$Variable.Name == 'HW.SmTree.frac.of.other' & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO2) + (VarDefs$Value[VarDefs$Variable.Name == 'HW.bark.frac.of.other' & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == 'Bark.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'] * global.vars$FlamingCO2)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 38 & SourceSink$SeverityClass == 'Mod'] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'Mod'] * global.vars$FlamingCO2 +  
  VarDefs$Value[VarDefs$Variable.Name == 'HW.stumps.frac.of.other' & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO2 + (VarDefs$Value[VarDefs$Variable.Name == 'Unburned.litter.area' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']*VarDefs$Value[VarDefs$Variable.Name == 'HW.SmTree.frac.of.other' & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO2) + (VarDefs$Value[VarDefs$Variable.Name == 'HW.bark.frac.of.other' & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == 'Bark.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'] * global.vars$FlamingCO2)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 38 & SourceSink$SeverityClass == 'High'] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'High'] * global.vars$FlamingCO2 +  
  VarDefs$Value[VarDefs$Variable.Name == 'HW.stumps.frac.of.other' & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO2 + (VarDefs$Value[VarDefs$Variable.Name == 'Unburned.litter.area' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']*VarDefs$Value[VarDefs$Variable.Name == 'HW.SmTree.frac.of.other' & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO2) + (VarDefs$Value[VarDefs$Variable.Name == 'HW.bark.frac.of.other' & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == 'Bark.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'] * global.vars$FlamingCO2)

#FluxID: 39
#Source: HW Other
#sink: CH4
#PLS: Proportional Combustion sum of branches, stumps, small trees and bark (mix of flaming and smouldering)
#Pseudocode:   (Flux10*FlamingCH4)+
# (Stumps.frac.of.other*DOM.Comb.Rate*SmoulderingCH4)+
# (Litter.frac.burned*SmTree.frac.other*FlamingCH4)+
# (Bark.frac.other*Bark.Comb.Frac*FlamingCH4)

#Notes:  works so far and gives reasonable values of ~0.017, 0.019, 0.02

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 39 & SourceSink$SeverityClass == 'Low'] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'Low'] * global.vars$FlamingCH4 +  
  VarDefs$Value[VarDefs$Variable.Name == 'HW.stumps.frac.of.other' & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCH4 + (VarDefs$Value[VarDefs$Variable.Name == 'Unburned.litter.area' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']*VarDefs$Value[VarDefs$Variable.Name == 'HW.SmTree.frac.of.other' & VarDefs$Ecozone == ecozone]*global.vars$FlamingCH4) + (VarDefs$Value[VarDefs$Variable.Name == 'HW.bark.frac.of.other' & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == 'Bark.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'] * global.vars$FlamingCH4)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 39 & SourceSink$SeverityClass == 'Mod'] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'Mod'] * global.vars$FlamingCH4 +  
  VarDefs$Value[VarDefs$Variable.Name == 'HW.stumps.frac.of.other' & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCH4 + (VarDefs$Value[VarDefs$Variable.Name == 'Unburned.litter.area' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']*VarDefs$Value[VarDefs$Variable.Name == 'HW.SmTree.frac.of.other' & VarDefs$Ecozone == ecozone]*global.vars$FlamingCH4) + (VarDefs$Value[VarDefs$Variable.Name == 'HW.bark.frac.of.other' & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == 'Bark.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'] * global.vars$FlamingCH4)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 39 & SourceSink$SeverityClass == 'High'] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'High'] * global.vars$FlamingCH4 +  
  VarDefs$Value[VarDefs$Variable.Name == 'HW.stumps.frac.of.other' & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCH4 + (VarDefs$Value[VarDefs$Variable.Name == 'Unburned.litter.area' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']*VarDefs$Value[VarDefs$Variable.Name == 'HW.SmTree.frac.of.other' & VarDefs$Ecozone == ecozone]*global.vars$FlamingCH4) + (VarDefs$Value[VarDefs$Variable.Name == 'HW.bark.frac.of.other' & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == 'Bark.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'] * global.vars$FlamingCH4)

#FluxID: 40
#Source: HW Other
#sink: CO
#PLS: Proportional Combustion sum of branches, stumps, small trees and bark (mix of flaming and smouldering)
#Pseudocode:   (Flux10*FlamingCO)+
# (Stumps.frac.of.other*DOM.Comb.Rate*SmoulderingCO)+
# (Litter.frac.burned*SmTree.frac.other*FlamingCO)+
# (Bark.frac.other*Bark.Comb.Frac*FlamingCO)

#Notes:  works so far 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 40 & SourceSink$SeverityClass == 'Low'] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'Low'] * global.vars$FlamingCO +  
  VarDefs$Value[VarDefs$Variable.Name == 'HW.stumps.frac.of.other' & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO + (VarDefs$Value[VarDefs$Variable.Name == 'Unburned.litter.area' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']*VarDefs$Value[VarDefs$Variable.Name == 'HW.SmTree.frac.of.other' & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO) + (VarDefs$Value[VarDefs$Variable.Name == 'HW.bark.frac.of.other' & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == 'Bark.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'] * global.vars$FlamingCO)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 40 & SourceSink$SeverityClass == 'Mod'] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'Mod'] * global.vars$FlamingCO +  
  VarDefs$Value[VarDefs$Variable.Name == 'HW.stumps.frac.of.other' & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO + (VarDefs$Value[VarDefs$Variable.Name == 'Unburned.litter.area' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']*VarDefs$Value[VarDefs$Variable.Name == 'HW.SmTree.frac.of.other' & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO) + (VarDefs$Value[VarDefs$Variable.Name == 'HW.bark.frac.of.other' & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == 'Bark.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'] * global.vars$FlamingCO)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 40 & SourceSink$SeverityClass == 'High'] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 37 & SourceSink$SeverityClass == 'High'] * global.vars$FlamingCO +  
  VarDefs$Value[VarDefs$Variable.Name == 'HW.stumps.frac.of.other' & VarDefs$Ecozone == ecozone] * as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]) * global.vars$SmoulderingCO + (VarDefs$Value[VarDefs$Variable.Name == 'Unburned.litter.area' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']*VarDefs$Value[VarDefs$Variable.Name == 'HW.SmTree.frac.of.other' & VarDefs$Ecozone == ecozone]*global.vars$FlamingCO) + (VarDefs$Value[VarDefs$Variable.Name == 'HW.bark.frac.of.other' & VarDefs$Ecozone == ecozone] * VarDefs$Value[VarDefs$Variable.Name == 'Bark.Comb.Frac' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'] * global.vars$FlamingCO)





#FluxID: 41
#Source: HW SubMerch
#sink: HW SubMerch
#PLS: Understory conifer survival rate
#Pseudocode:  =1-(mortality of submerch conifers in severity class) 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 41 & SourceSink$SeverityClass == 'Low'] <- 1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.SubMerch.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 41 & SourceSink$SeverityClass == 'Mod'] <- 1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.SubMerch.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 41 & SourceSink$SeverityClass == 'High'] <- 1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.SubMerch.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']


#FluxID: 42
#Source: HW SubMerch
#sink: HW Branch Snag
#PLS: Understory conifer stems killed but not consumed
#Pseudocode:  = SubMerch mortality, since live understory trees don't get consumed in the fire, 

#notes: submerch trees assumed to not have large enough branches to avoid consumption in fire.  Equal to 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 42 & SourceSink$SeverityClass == 'Low'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.SubMerch.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 42 & SourceSink$SeverityClass == 'Mod'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.SubMerch.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 42 & SourceSink$SeverityClass == 'High'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.SubMerch.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']


#FluxID: 43
#Source: HW SubMerch
#sink: CO2
#PLS: Understory Conifer consumption rate
#Pseudocode:  = 0 !IF! this is only about submerch stems 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 43 & SourceSink$SeverityClass == 'Low'] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 43 & SourceSink$SeverityClass == 'Mod'] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 43 & SourceSink$SeverityClass == 'High'] <- 0

#FluxID: 44
#Source: HW SubMerch
#sink: CH4
#PLS: Understory Conifer consumption rate
#Pseudocode:  = 0 !IF! this is only about submerch stems 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 44 & SourceSink$SeverityClass == 'Low'] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 44 & SourceSink$SeverityClass == 'Mod'] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 44 & SourceSink$SeverityClass == 'High'] <- 0


#FluxID: 45
#Source: HW SubMerch
#sink: CO
#PLS: Understory Conifer consumption rate
#Pseudocode:  = 0 !IF! this is only about submerch stems 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 45 & SourceSink$SeverityClass == 'Low'] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 45 & SourceSink$SeverityClass == 'Mod'] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 45 & SourceSink$SeverityClass == 'High'] <- 0

#FluxID: 46
#Source: HW Coarse roots
#sink: HW Coarse roots
#PLS: Surviving coarse roots in conifers
#Pseudocode:  =1-((HW mortality rate)*(1-HW Resprout Rate))

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 46 & SourceSink$SeverityClass == 'Low'] <- 1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']* (1-VarDefs$Value[VarDefs$Variable.Name == 'HW.ReSprout' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 46 & SourceSink$SeverityClass == 'Mod'] <- 1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']* (1-VarDefs$Value[VarDefs$Variable.Name == 'HW.ReSprout' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 46 & SourceSink$SeverityClass == 'High'] <- 1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']* (1-VarDefs$Value[VarDefs$Variable.Name == 'HW.ReSprout' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'])

#FluxID: 47
#Source: HW Coarse roots
#sink: Above Ground Fast DOM
#PLS: Coarse Roots killed in fire but not combusted in organic soil
#Pseudocode:  =(HW mortality rate*(1-HW Resproute Rate))*(conifer coarse root fraction in organic soil)
#Note: assuming even if duff burns, coarse live roots don't burn alongsides HW.prop.Coarse.Root.duff

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 47 & SourceSink$SeverityClass == 'Low'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low']* (1-VarDefs$Value[VarDefs$Variable.Name == 'HW.ReSprout' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'])* VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Coarse.Root.duff' & VarDefs$Ecozone == ecozone]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 47 & SourceSink$SeverityClass == 'Mod'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod']* (1-VarDefs$Value[VarDefs$Variable.Name == 'HW.ReSprout' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'])* VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Coarse.Root.duff' & VarDefs$Ecozone == ecozone]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 47 & SourceSink$SeverityClass == 'High'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High']* (1-VarDefs$Value[VarDefs$Variable.Name == 'HW.ReSprout' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'])* VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Coarse.Root.duff' & VarDefs$Ecozone == ecozone]


#FluxID: 48
#Source: HW Coarse roots
#sink: Below Ground Fast DOM
#PLS: Coarse Roots killed in fire but not combusted since they are in mineral soil
#Pseudocode:  =(conifer mortality rate)*(1-HW ReSprout rate)*(conifer coarse root fraction in mineral soil)
#Note: assuming even if duff burns, coarse live roots don't burn alongsides HW.prop.Coarse.Root.duff

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 48 & SourceSink$SeverityClass == 'Low'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'] * (1-VarDefs$Value[VarDefs$Variable.Name == 'HW.ReSprout' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'])*(1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Coarse.Root.duff' & VarDefs$Ecozone == ecozone])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 48 & SourceSink$SeverityClass == 'Mod'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'] * (1-VarDefs$Value[VarDefs$Variable.Name == 'HW.ReSprout' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'])*(1 -  VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Coarse.Root.duff' & VarDefs$Ecozone == ecozone])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 48 & SourceSink$SeverityClass == 'High'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'] * (1-VarDefs$Value[VarDefs$Variable.Name == 'HW.ReSprout' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'])*(1 -  VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Coarse.Root.duff' & VarDefs$Ecozone == ecozone])




#FluxID: 50
#Source: HW fine roots
#sink: Above Ground Very Fast DOM
#PLS: Fine roots killed but not burned in organic soil
#Pseudocode:  =(conifer mortality rate)*(1-HW ReSprout rate)*(fine root fraction in organic soil)*(1-fraction of duff consumed)
#notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 50 & SourceSink$SeverityClass == 'Low'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'] * (1-VarDefs$Value[VarDefs$Variable.Name == 'HW.ReSprout' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'])*VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(1 - as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]))

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 50 & SourceSink$SeverityClass == 'Mod'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'] * (1-VarDefs$Value[VarDefs$Variable.Name == 'HW.ReSprout' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'])*VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(1 - as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]))

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 50 & SourceSink$SeverityClass == 'High'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'] * (1-VarDefs$Value[VarDefs$Variable.Name == 'HW.ReSprout' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'])*VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(1 - as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]))


#FluxID: 51
#Source: HW fine roots
#sink: Below Ground Very Fast DOM
#PLS: Fine roots killed but not burned in mineral soil
#Pseudocode:  =(conifer mortality rate)*(1-HW ReSprout rate)*(fine root fraction in mineral soil)
#notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 51 & SourceSink$SeverityClass == 'Low'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'] * (1-VarDefs$Value[VarDefs$Variable.Name == 'HW.ReSprout' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Low'])*(1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 51 & SourceSink$SeverityClass == 'Mod'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'] * (1-VarDefs$Value[VarDefs$Variable.Name == 'HW.ReSprout' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'Mod'])*(1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 51 & SourceSink$SeverityClass == 'High'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.Mort' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'] * (1-VarDefs$Value[VarDefs$Variable.Name == 'HW.ReSprout' & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == 'High'])*(1 - VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone])




#FluxID: 52
#Source: HW fine roots
#sink: CO2
#PLS: Fine roots combusted in duff
#Pseudocode:  =(conifer mortality rate)*(fine root fraction in organic soil)*(1-fraction of duff consumed)
#notes: since this is solely based on FFFC fraction, which isn't itself severity driven, there's no severity gradient in here.  Note also no relation to HW mortality (since you can burn off roots and not actually kill the tree, to a point)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 52 & SourceSink$SeverityClass == 'Low'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 52 & SourceSink$SeverityClass == 'Mod'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 52 & SourceSink$SeverityClass == 'High'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO2


#FluxID: 53
#Source: HW fine roots
#sink: CH4
#PLS: Fine roots combusted in duff
#Pseudocode:  =(conifer mortality rate)*(fine root fraction in organic soil)*(1-fraction of duff consumed)
#notes: since this is solely based on FFFC fraction, which isn't itself severity driven, there's no severity gradient in here.  Note also no relation to HW mortality (since you can burn off roots and not actually kill the tree, to a point)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 53 & SourceSink$SeverityClass == 'Low'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 53 & SourceSink$SeverityClass == 'Mod'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 53 & SourceSink$SeverityClass == 'High'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCH4



#FluxID: 54
#Source: HW fine roots
#sink: CO
#PLS: Fine roots combusted in duff
#Pseudocode:  =(conifer mortality rate)*(fine root fraction in organic soil)*(1-fraction of duff consumed)
#notes: since this is solely based on FFFC fraction, which isn't itself severity driven, there's no severity gradient in here.  Note also no relation to HW mortality (since you can burn off roots and not actually kill the tree, to a point)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 54 & SourceSink$SeverityClass == 'Low'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 54 & SourceSink$SeverityClass == 'Mod'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 54 & SourceSink$SeverityClass == 'High'] <- VarDefs$Value[VarDefs$Variable.Name == 'HW.prop.Fine.Root.duff' & VarDefs$Ecozone == ecozone]*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])) * global.vars$SmoulderingCO







### end hardwoods


#FluxID: 55
#Source: Aboveground Very Fast DOM
#sink: Aboveground Very Fast DOM
#PLS: Unburned fraction of The L horizonb comprised of foliar litter plus dead fine roots, approximately <5 mm diameter
#Pseudocode:  =Unburned.litter.area(from plot data)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 55 & SourceSink$SeverityClass == "Low"] <-  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 55 & SourceSink$SeverityClass == "Mod"] <-  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 55 & SourceSink$SeverityClass == "High"] <-  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]


#FluxID: 56
#Source: Aboveground Very Fast DOM
#sink: CO2
#PLS: Burned fraction of The L horizonb comprised of foliar litter plus dead fine roots, approximately <5 mm diameter
#Pseudocode:  =1-Unburned.litter.area(from plot data)*Flaming

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 56 & SourceSink$SeverityClass == "Low"] <- (1 -  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])*global.vars$FlamingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 56 & SourceSink$SeverityClass == "Mod"] <- (1 -  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])*global.vars$FlamingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 56 & SourceSink$SeverityClass == "High"] <- (1 -  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])*global.vars$FlamingCO2


#FluxID: 57
#Source: Aboveground Very Fast DOM
#sink: CH4
#PLS: Burned fraction of The L horizonb comprised of foliar litter plus dead fine roots, approximately <5 mm diameter
#Pseudocode:  =1-Unburned.litter.area(from plot data)*Flaming

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 57 & SourceSink$SeverityClass == "Low"] <- (1 -  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])*global.vars$FlamingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 57 & SourceSink$SeverityClass == "Mod"] <- (1 -  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])*global.vars$FlamingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 57 & SourceSink$SeverityClass == "High"] <- (1 -  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])*global.vars$FlamingCH4


#FluxID: 58
#Source: Aboveground Very Fast DOM
#sink: CO
#PLS: Burned fraction of The L horizonb comprised of foliar litter plus dead fine roots, approximately <5 mm diameter
#Pseudocode:  =1-Unburned.litter.area(from plot data)*Flaming

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 58 & SourceSink$SeverityClass == "Low"] <- (1 -  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])*global.vars$FlamingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 58 & SourceSink$SeverityClass == "Mod"] <- (1 -  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])*global.vars$FlamingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 58 & SourceSink$SeverityClass == "High"] <- (1 -  VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])*global.vars$FlamingCO


#FluxID: 59
#Source: Belowground Very Fast DOM
#sink: Belowground Very Fast DOM
#PLS: Uncombusted Fraction of Dead fine roots in the mineral soil, approximately <5 mm diameter
#Pseudocode:  == 1, since dead roots in the mineral soil are not combusted

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 59 & SourceSink$SeverityClass == "Low"] <- 1 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 59 & SourceSink$SeverityClass == "Mod"] <- 1

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 59 & SourceSink$SeverityClass == "High"] <- 1

#FluxID: 60
#Source: Aboveground Fast DOM
#sink: Above Ground Fast DOM
#PLS: Uncombusted Fine and small woody debris plus dead coarse roots in the forest floor, approximately ≥5 and <75 mm diameter
#Pseudocode: =[(litter surface area fraction unburned*woody debris portion of AGFastDOM)+(Dead coarse root fraction of AGFastDOM*(fraction of duff consumed)]
#*Assume all woody fine+small woody debris is combusted, but only fractional combustion of dead coarse roots alongside duff
#CWD.frac.of.AGFastDOM

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "Low"] <- (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]*VarDefs$Value[VarDefs$Variable.Name == "CWD.frac.of.AGFastDOM" & VarDefs$Ecozone == ecozone] + ((1 - VarDefs$Value[VarDefs$Variable.Name == "CWD.frac.of.AGFastDOM" & VarDefs$Ecozone == ecozone])*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]))))

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "Mod"] <-  (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]*VarDefs$Value[VarDefs$Variable.Name == "CWD.frac.of.AGFastDOM" & VarDefs$Ecozone == ecozone] + ((1 - VarDefs$Value[VarDefs$Variable.Name == "CWD.frac.of.AGFastDOM" & VarDefs$Ecozone == ecozone])*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]))))

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "High"] <- (VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]*VarDefs$Value[VarDefs$Variable.Name == "CWD.frac.of.AGFastDOM" & VarDefs$Ecozone == ecozone] + ((1 - VarDefs$Value[VarDefs$Variable.Name == "CWD.frac.of.AGFastDOM" & VarDefs$Ecozone == ecozone])*(as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]))))


#FluxID: 61
#Source: Aboveground Fast DOM
#sink: CO2
#PLS: Combusted Fine and small woody debris plus dead coarse roots in the forest floor, approximately ≥5 and <75 mm diameter
#Pseudocode: = flux60*smouldering


SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 61 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "Low"])*global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 61 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "Mod"])*global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 61 & SourceSink$SeverityClass == "High"] <- (1 -  SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "High"])*global.vars$SmoulderingCO2

#FluxID: 62
#Source: Aboveground Fast DOM
#sink: CH4
#PLS: Combusted Fine and small woody debris plus dead coarse roots in the forest floor, approximately ≥5 and <75 mm diameter
#Pseudocode: = flux60*smouldering


SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 62 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "Low"])*global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 62 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "Mod"])*global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 62 & SourceSink$SeverityClass == "High"] <- (1 -  SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "High"])*global.vars$SmoulderingCH4

#FluxID: 63
#Source: Aboveground Fast DOM
#sink: CO
#PLS: Combusted Fine and small woody debris plus dead coarse roots in the forest floor, approximately ≥5 and <75 mm diameter
#Pseudocode: = flux60*smouldering


SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 63 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "Low"])*global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 63 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "Mod"])*global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 63 & SourceSink$SeverityClass == "High"] <- (1 -  SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 60 & SourceSink$SeverityClass == "High"])*global.vars$SmoulderingCO

#FluxID: 64
#Source: Belowground Fast DOM
#sink: Below Ground Fast DOM
#PLS: Uncombusted fraction of Dead coarse roots in the mineral soil, approximately ≥5 diameter
#Pseudocode: =~ 1, since no combustion within mineral soil

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 64 & SourceSink$SeverityClass == "Low"] <- 1
SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 64 & SourceSink$SeverityClass == "Mod"] <- 1
SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 64 & SourceSink$SeverityClass == "High"] <- 1

#FluxID: 65
#Source: Medium DOM
#sink: Medium DOM
#PLS: Uncombusted Coarse woody debris on the ground
#Pseudocode: =(1-unburned litter area)*(1-MedDOM.Comb.Frac)
#note: could be from field data, here assuming burns at same rate as duff

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "Low"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])*(1 - VarDefs$Value[VarDefs$Variable.Name == "MedDOM.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]) 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "Mod"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])*(1 - VarDefs$Value[VarDefs$Variable.Name == "MedDOM.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]) 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "High"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "Unburned.litter.area" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])*(1 - VarDefs$Value[VarDefs$Variable.Name == "MedDOM.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]) 

#FluxID: 66
#Source: Medium DOM
#sink: CO2
#PLS: Combusted Coarse woody debris on the ground
#Pseudocode: =(1-Flux65)*smoulderingCO2
#note: could be from field data, here assuming burns at same rate as duff
#high values are probably on the high end, would need field data

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 66 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "Low"])*global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 66 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "Mod"])*global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 66 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "High"])*global.vars$SmoulderingCO2

#FluxID: 67
#Source: Medium DOM
#sink: CH4
#PLS: Combusted Coarse woody debris on the ground
#Pseudocode: =(1-(fraction of duff consumed))*(1-unburned litter area)*smouldering
#note: could be from field data, here assuming burns at same rate as duff
#high values are probably on the high end, would need field data

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 67 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "Low"])*global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 67 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "Mod"])*global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 67 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "High"])*global.vars$SmoulderingCH4


#FluxID: 68
#Source: Medium DOM
#sink: CO
#PLS: Combusted Coarse woody debris on the ground
#Pseudocode: =(1-(fraction of duff consumed))*(1-unburned litter area)*smouldering
#note: could be from field data, here assuming burns at same rate as duff
#high values are probably on the high end, would need field data

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 68 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "Low"])*global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 68 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "Mod"])*global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 68 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 65 & SourceSink$SeverityClass == "High"])*global.vars$SmoulderingCO



#FluxID: 69
#Source: Medium DOM
#sink: Black Carbon
#PLS: Coarse woody debris on the ground converted to black carbon
#Pseudocode: =0 (until field data given)
#note: could be from field data, here assuming burns at same rate as duff
#high values are probably on the high end, would need field data (or at least Koroscil MSc lab data)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 69 & SourceSink$SeverityClass == "Low"] <- 0
SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 69 & SourceSink$SeverityClass == "Mod"] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 69 & SourceSink$SeverityClass == "High"] <- 0


#FluxID: 70
#Source: Aboveground Slow DOM
#sink: Above Ground slow DOM
#PLS: Uncombusted fraction of duff horizons
#Pseudocode: =1-(fraction of duff consumed)
#note: see CaMP for slow DOM in peat layers

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "Low"] <- (1 - (as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone]))) 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "Mod"] <- (1 - (as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])))

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "High"] <- (1 - (as.numeric(FFFC$Duff.consump.frac[FFFC$Ecozone == ecozone])))


#FluxID: 71
#Source: Aboveground Slow DOM
#sink: CO2
#PLS: Combusted Fraction of duff horizons
#Pseudocode: =(fraction of duff consumed)*Smouldering


SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 71 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "Low"])*global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 71 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "Mod"])*global.vars$SmoulderingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 71 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "High"])*global.vars$SmoulderingCO2

#FluxID: 72
#Source: Aboveground Slow DOM
#sink: CH4
#PLS: Combusted Fraction of duff horizons
#Pseudocode: ==(fraction of duff consumed)*Smouldering

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 72 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "Low"])*global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 72 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "Mod"])*global.vars$SmoulderingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 72 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "High"])*global.vars$SmoulderingCH4


#FluxID: 73
#Source: Aboveground Slow DOM
#sink: CO
#PLS: Combusted Fraction of duff horizons
#Pseudocode: =(fraction of duff consumed)*Smouldering

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 73 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "Low"])*global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 73 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "Mod"])*global.vars$SmoulderingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 73 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 70 & SourceSink$SeverityClass == "High"])*global.vars$SmoulderingCO


#FluxID: 74
#Source: Belowground Slow DOM
#sink: Below Ground Slow DOM
#PLS: Uncombusted fraction of Humified organic matter in the mineral soil
#Pseudocode: == 1
#notes: no combustion 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 74 & SourceSink$SeverityClass == "Low"] <- 1

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 74 & SourceSink$SeverityClass == "Mod"] <- 1

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 74 & SourceSink$SeverityClass == "High"] <- 1

#FluxID: 75
#Source: Softwood Stem Snag
#sink: Medium DOM
#PLS: Fraction of conifer snags that fall to ground but not combusted (i.e. fall after the passage of the fire and due to the fire)
#Pseudocode: =[1-(SW.Snag.Comb.Frac]*(Snag.Fall.Frac)
#notes: assume no combustion of these snags otherwise

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "Low"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]) * VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "Mod"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]) * VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "High"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]) * VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]


#FluxID: 76
#Source: Softwood Stem Snag
#sink: Softwood Stem Snag
#PLS: Uncombusted fraction of conifer snags (still upright)
#Pseudocode: =[1-(SW.Snag.Comb.Frac)]*(1-Snag.Fall.Frac)
#notes: assume no combustion of these snags otherwise

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "Low"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]) * (1 - VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "Mod"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]) * (1 - VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "High"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]) * (1 - VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])

#FluxID: 77
#Source: Softwood Stem Snag
#sink: CO2
#PLS: Uncombusted fraction of conifer snags (still upright)
#Pseudocode: =[1-SW.Snag.Comb.Frac-Snag.Fall.Frac)*Flaming
#notes: assume no combustion of these snags otherwise

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 77 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "Low"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "Low"])*global.vars$FlamingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 77 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "Mod"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "Mod"])*global.vars$FlamingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 77 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "High"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "High"])*global.vars$FlamingCO2

#FluxID: 78
#Source: Softwood Stem Snag
#sink: CH4
#PLS: Uncombusted fraction of conifer snags (still upright)
#Pseudocode: =[1-SW.Snag.Comb.Frac-Snag.Fall.Frac)*Flaming
#notes: snags not remaining upright nor fallen down are combusted

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 78 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "Low"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "Low"])*global.vars$FlamingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 78 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "Mod"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "Mod"])*global.vars$FlamingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 78 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "High"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "High"])*global.vars$FlamingCH4


#FluxID: 79
#Source: Softwood Stem Snag
#sink: CO
#PLS: Uncombusted fraction of conifer snags (still upright)
#Pseudocode: =[1-SW.Snag.Comb.Frac-Snag.Fall.Frac)*SW.Snag.Comb.Frac*Flaming
#notes: snags not remaining upright nor fallen down are combusted

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 79 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "Low"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "Low"])*global.vars$FlamingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 79 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "Mod"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "Mod"])*global.vars$FlamingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 79 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 75 & SourceSink$SeverityClass == "High"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 76 & SourceSink$SeverityClass == "High"])*global.vars$FlamingCO

#FluxID: 80
#Source: Softwood Stem Snag
#sink: Black Carbon
#PLS: Uncombusted fraction of conifer snags (still upright)
#Pseudocode: =[1-SW.Snag.Comb.Frac-Snag.Fall.Frac)*BlackCarbon
#notes: no black carbon production for now, will need to estimate based on field data

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 80 & SourceSink$SeverityClass == "Low"] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 80 & SourceSink$SeverityClass == "Mod"] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 80 & SourceSink$SeverityClass == "High"] <- 0


#FluxID: 81
#Source: Softwood Branch Snag
#sink: Above Ground Fast DOM
#PLS: Portion of conifer snag branches that falls onto the ground
#Pseudocode: =[1-(SW.Snag.BW.Comb.Frac)]*Snag.Fall.Frac
#notes: Assuming half of all unconsumed portions branches on snags fall to the ground, half of them remain on the snag.  No field data to this effect.  

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "Low"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.BW.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]) * VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "Mod"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.BW.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]) * VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "High"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.BW.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]) * VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]


#FluxID: 82
#Source: Softwood Branch Snag
#sink: Softwood Branch Snag
#PLS: Unaltered fraction of snag branches
#Pseudocode: =[1-(SW.Snag.BW.Comb.Frac)]*(1-Snag.Fall.Frac)
#notes: Assuming half of all unconsumed portions branches on snags fall to the ground, half of them remain on the snag.  No field data to this effect.  

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "Low"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.BW.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]) * (1 - VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "Mod"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.BW.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]) * (1 - VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "High"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "SW.Snag.BW.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]) * (1 - VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])

#FluxID: 83
#Source: Softwood Branch Snag
#sink: CO2
#PLS: Combusted fraction of snag branches
#Pseudocode: = (SW.Snag.BW.Comb.Frac)*(Snag.Fall.Frac)
#notes:   

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 83 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "Low"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "Low"])*global.vars$FlamingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 83 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "Mod"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "Mod"])*global.vars$FlamingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 83 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "High"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "High"])*global.vars$FlamingCO2


#FluxID: 84
#Source: Softwood Branch Snag
#sink: CH4
#PLS: Combusted fraction of snag branches
#Pseudocode: = (SW.Snag.BW.Comb.Frac)*(Snag.Fall.Frac)
#notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 84 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "Low"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "Low"])*global.vars$FlamingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 84 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "Mod"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "Mod"])*global.vars$FlamingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 84 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "High"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "High"])*global.vars$FlamingCH4



#FluxID: 85
#Source: Softwood Branch Snag
#sink: CO
#PLS: Combusted fraction of snag branches
#Pseudocode: = (SW.Snag.BW.Comb.Frac)*(Snag.Fall.Frac)
#notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 85 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "Low"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "Low"])*global.vars$FlamingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 85 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "Mod"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "Mod"])*global.vars$FlamingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 85 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 81 & SourceSink$SeverityClass == "High"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 82 & SourceSink$SeverityClass == "High"])*global.vars$FlamingCO


#FluxID: 86
#Source: Hardwood Stem Snag
#sink: Medium DOM
#PLS: Fraction of deciduous snags that fall to ground but not combusted (i.e. fall after the passage of the fire and due to the fire)
#Pseudocode: =[1-(HW.Snag.Comb.Frac]*(Snag.Fall.Frac)
#notes: assume no combustion of these snags otherwise

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 86 & SourceSink$SeverityClass == "Low"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "HW.Snag.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]) * VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 86 & SourceSink$SeverityClass == "Mod"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "HW.Snag.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]) * VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 86 & SourceSink$SeverityClass == "High"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "HW.Snag.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]) * VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]


#FluxID: 87
#Source: Hardwood Stem Snag
#sink: Hardwood Stem Snag
#PLS: Uncombusted fraction of deciduous snags (still upright)
#Pseudocode: =[1-(HW.Snag.Comb.Frac)]*(1-Snag.Fall.Frac)
#notes: assume no combustion of these snags otherwise

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 87 & SourceSink$SeverityClass == "Low"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "HW.Snag.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]) * (1 - VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 87 & SourceSink$SeverityClass == "Mod"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "HW.Snag.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]) * (1 - VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 87 & SourceSink$SeverityClass == "High"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "HW.Snag.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]) * (1 - VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])

#FluxID: 88
#Source: Hardwood Stem Snag
#sink: CO2
#PLS: Uncombusted fraction of deciduous snags (still upright)
#Pseudocode: =[1-HW.Snag.Comb.Frac-Snag.Fall.Frac)*Flaming
#notes: assume no combustion of these snags otherwise

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 88 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 86 & SourceSink$SeverityClass == "Low"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 87 & SourceSink$SeverityClass == "Low"])*global.vars$FlamingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 88 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 86 & SourceSink$SeverityClass == "Mod"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 87 & SourceSink$SeverityClass == "Mod"])*global.vars$FlamingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 88 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 86 & SourceSink$SeverityClass == "High"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 87 & SourceSink$SeverityClass == "High"])*global.vars$FlamingCO2

#FluxID: 89
#Source: Hardwood Stem Snag
#sink: CH4
#PLS: Uncombusted fraction of deciduous snags (still upright)
#Pseudocode: =[1-HW.Snag.Comb.Frac-Snag.Fall.Frac)*Flaming
#notes: snags not remaining upright nor fallen down are combusted

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 89 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 86 & SourceSink$SeverityClass == "Low"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 87 & SourceSink$SeverityClass == "Low"])*global.vars$FlamingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 89 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 86 & SourceSink$SeverityClass == "Mod"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 87 & SourceSink$SeverityClass == "Mod"])*global.vars$FlamingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 89 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 86 & SourceSink$SeverityClass == "High"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 87 & SourceSink$SeverityClass == "High"])*global.vars$FlamingCH4


#FluxID: 90
#Source: Hardwood Stem Snag
#sink: CO
#PLS: Uncombusted fraction of deciduous snags (still upright)
#Pseudocode: =[1-HW.Snag.Comb.Frac-Snag.Fall.Frac)*HW.Snag.Comb.Frac*Flaming
#notes: snags not remaining upright nor fallen down are combusted

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 90 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 86 & SourceSink$SeverityClass == "Low"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 87 & SourceSink$SeverityClass == "Low"])*global.vars$FlamingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 90 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 86 & SourceSink$SeverityClass == "Mod"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 87 & SourceSink$SeverityClass == "Mod"])*global.vars$FlamingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 90 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 86 & SourceSink$SeverityClass == "High"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 87 & SourceSink$SeverityClass == "High"])*global.vars$FlamingCO

#FluxID: 91
#Source: Hardwood Stem Snag
#sink: Black Carbon
#PLS: Uncombusted fraction of deciduous snags (still upright)
#Pseudocode: =[1-HW.Snag.Comb.Frac-Snag.Fall.Frac)*BlackCarbon
#notes: no black carbon production for now, will need to estimate based on field data

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 91 & SourceSink$SeverityClass == "Low"] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 91 & SourceSink$SeverityClass == "Mod"] <- 0

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 91 & SourceSink$SeverityClass == "High"] <- 0


#FluxID: 92
#Source: Hardwood Branch Snag
#sink: Above Ground Fast DOM
#PLS: Portion of deciduous snag branches that falls onto the ground
#Pseudocode: =[1-(HW.Snag.BW.Comb.Frac)]*Snag.Fall.Frac
#notes: Assuming half of all unconsumed portions branches on snags fall to the ground, half of them remain on the snag.  No field data to this effect.  

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 92 & SourceSink$SeverityClass == "Low"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "HW.Snag.BW.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]) * VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 92 & SourceSink$SeverityClass == "Mod"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "HW.Snag.BW.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]) * VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 92 & SourceSink$SeverityClass == "High"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "HW.Snag.BW.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]) * VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]


#FluxID: 93
#Source: Hardwood Branch Snag
#sink: Hardwood Branch Snag
#PLS: Unaltered fraction of snag branches
#Pseudocode: =[1-(HW.Snag.BW.Comb.Frac)]*(1-Snag.Fall.Frac)
#notes: Assuming half of all unconsumed portions branches on snags fall to the ground, half of them remain on the snag.  No field data to this effect.  

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 93 & SourceSink$SeverityClass == "Low"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "HW.Snag.BW.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"]) * (1 - VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Low"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 93 & SourceSink$SeverityClass == "Mod"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "HW.Snag.BW.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"]) * (1 - VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "Mod"])

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 93 & SourceSink$SeverityClass == "High"] <- (1 - VarDefs$Value[VarDefs$Variable.Name == "HW.Snag.BW.Comb.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"]) * (1 - VarDefs$Value[VarDefs$Variable.Name == "Snag.Fall.Frac" & VarDefs$Ecozone == ecozone & VarDefs$SeverityClass == "High"])

#FluxID: 94
#Source: Hardwood Branch Snag
#sink: CO2
#PLS: Combusted fraction of snag branches
#Pseudocode: = (HW.Snag.BW.Comb.Frac)*(Snag.Fall.Frac)
#notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 94 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 92 & SourceSink$SeverityClass == "Low"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 93 & SourceSink$SeverityClass == "Low"])*global.vars$FlamingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 94 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 92 & SourceSink$SeverityClass == "Mod"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 93 & SourceSink$SeverityClass == "Mod"])*global.vars$FlamingCO2

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 94 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 92 & SourceSink$SeverityClass == "High"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 93 & SourceSink$SeverityClass == "High"])*global.vars$FlamingCO2


#FluxID: 95
#Source: Hardwood Branch Snag
#sink: CH4
#PLS: Combusted fraction of snag branches
#Pseudocode: = (HW.Snag.BW.Comb.Frac)*(Snag.Fall.Frac)
#notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 95 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 92 & SourceSink$SeverityClass == "Low"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 93 & SourceSink$SeverityClass == "Low"])*global.vars$FlamingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 95 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 92 & SourceSink$SeverityClass == "Mod"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 93 & SourceSink$SeverityClass == "Mod"])*global.vars$FlamingCH4

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 95 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 92 & SourceSink$SeverityClass == "High"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 93 & SourceSink$SeverityClass == "High"])*global.vars$FlamingCH4



#FluxID: 96
#Source: Hardwood Branch Snag
#sink: CO
#PLS: Combusted fraction of snag branches
#Pseudocode: = (HW.Snag.BW.Comb.Frac)*(Snag.Fall.Frac)
#notes:  

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 96 & SourceSink$SeverityClass == "Low"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 92 & SourceSink$SeverityClass == "Low"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 93 & SourceSink$SeverityClass == "Low"])*global.vars$FlamingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 96 & SourceSink$SeverityClass == "Mod"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 92 & SourceSink$SeverityClass == "Mod"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 93 & SourceSink$SeverityClass == "Mod"])*global.vars$FlamingCO

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 96 & SourceSink$SeverityClass == "High"] <- (1 - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 92 & SourceSink$SeverityClass == "High"] - SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 93 & SourceSink$SeverityClass == "High"])*global.vars$FlamingCO

### Black Carbon -> black carbon and BC to atm emissions are FluxID 97-100

#FluxID: 101-117
#Source: misc
#sink: PM2.5
#PLS: Combustion emissions to 2.5 micron particulate matter
#Pseudocode: = CORefFluxID * (CO to PM/NMOG ratio)
#notes:  

###now, loop through the PM2.5, PM10, and NMOG EFs, using the ratio of PM:CO(or NMOG) and phase to define them in bulk:

###do this in a loop for the PM2.5 range:

## here is the fluxID of interest to grab the CO of:

for(FluxIDLoop in seq(from=101,to=117)){
  
  ### this a.low placeholder grabs the reference CO DM value, which we then multiply against the CO:PM25 ratio in order to get the PM
a.low <- SourceSink$CORefFluxID[SourceSink$FluxID == FluxIDLoop & SourceSink$SeverityClass == "Low" & SourceSink$Ecozone == ecozone]

a.mod <- SourceSink$CORefFluxID[SourceSink$FluxID == FluxIDLoop & SourceSink$SeverityClass == "Mod" & SourceSink$Ecozone == ecozone]

a.high <- SourceSink$CORefFluxID[SourceSink$FluxID == FluxIDLoop & SourceSink$SeverityClass == "High" & SourceSink$Ecozone == ecozone]


SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == FluxIDLoop & SourceSink$SeverityClass == "Low"] <-
SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == a.low & SourceSink$SeverityClass == "Low"]*ifelse(unique(SourceSink$Phase[SourceSink$FluxID == FluxIDLoop]) == "Flaming",global.vars$FlamingPM25/global.vars$FlamingCO,global.vars$SmoulderingPM25/global.vars$SmoulderingCO)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == FluxIDLoop & SourceSink$SeverityClass == "Mod"] <-
SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == a.mod & SourceSink$SeverityClass == "Mod"]*ifelse(unique(SourceSink$Phase[SourceSink$FluxID == FluxIDLoop]) == "Flaming",global.vars$FlamingPM25/global.vars$FlamingCO,global.vars$SmoulderingPM25/global.vars$SmoulderingCO)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == FluxIDLoop & SourceSink$SeverityClass == "High"] <-
SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == a.high & SourceSink$SeverityClass == "High"]*ifelse(unique(SourceSink$Phase[SourceSink$FluxID == FluxIDLoop]) == "Flaming",global.vars$FlamingPM25/global.vars$FlamingCO,global.vars$SmoulderingPM25/global.vars$SmoulderingCO)
}

#### now for PM10um

for(FluxIDLoop in seq(from=118,to=134)){
a.low <- SourceSink$CORefFluxID[SourceSink$FluxID == FluxIDLoop & SourceSink$SeverityClass == "Low" & SourceSink$Ecozone == ecozone]

a.mod <- SourceSink$CORefFluxID[SourceSink$FluxID == FluxIDLoop & SourceSink$SeverityClass == "Mod" & SourceSink$Ecozone == ecozone]

a.high <- SourceSink$CORefFluxID[SourceSink$FluxID == FluxIDLoop & SourceSink$SeverityClass == "High" & SourceSink$Ecozone == ecozone]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == FluxIDLoop & SourceSink$SeverityClass == "Low"] <-
SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == a.low & SourceSink$SeverityClass == "Low"]*ifelse(unique(SourceSink$Phase[SourceSink$FluxID == FluxIDLoop]) == "Flaming",global.vars$FlamingPM10/global.vars$FlamingCO,global.vars$SmoulderingPM10/global.vars$SmoulderingCO)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == FluxIDLoop & SourceSink$SeverityClass == "Mod"] <-
SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == a.mod & SourceSink$SeverityClass == "Mod"]*ifelse(unique(SourceSink$Phase[SourceSink$FluxID == FluxIDLoop]) == "Flaming",global.vars$FlamingPM10/global.vars$FlamingCO,global.vars$SmoulderingPM10/global.vars$SmoulderingCO)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == FluxIDLoop & SourceSink$SeverityClass == "High"] <-
SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == a.high & SourceSink$SeverityClass == "High"]*ifelse(unique(SourceSink$Phase[SourceSink$FluxID == FluxIDLoop]) == "Flaming",global.vars$FlamingPM10/global.vars$FlamingCO,global.vars$SmoulderingPM10/global.vars$SmoulderingCO)
}

###lastly, for NMOG

for(FluxIDLoop in seq(from=135,to=151)){
a.low <- SourceSink$CORefFluxID[SourceSink$FluxID == FluxIDLoop & SourceSink$SeverityClass == "Low" & SourceSink$Ecozone == ecozone]

a.mod <- SourceSink$CORefFluxID[SourceSink$FluxID == FluxIDLoop & SourceSink$SeverityClass == "Mod" & SourceSink$Ecozone == ecozone]

a.high <- SourceSink$CORefFluxID[SourceSink$FluxID == FluxIDLoop & SourceSink$SeverityClass == "High" & SourceSink$Ecozone == ecozone]

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == FluxIDLoop & SourceSink$SeverityClass == "Low"] <-
SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == a.low & SourceSink$SeverityClass == "Low"]*ifelse(unique(SourceSink$Phase[SourceSink$FluxID == FluxIDLoop]) == "Flaming",global.vars$FlamingNMOG/global.vars$FlamingCO,global.vars$SmoulderingNMOG/global.vars$SmoulderingCO)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == FluxIDLoop & SourceSink$SeverityClass == "Mod"] <-
SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == a.mod & SourceSink$SeverityClass == "Mod"]*ifelse(unique(SourceSink$Phase[SourceSink$FluxID == FluxIDLoop]) == "Flaming",global.vars$FlamingNMOG/global.vars$FlamingCO,global.vars$SmoulderingNMOG/global.vars$SmoulderingCO)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == FluxIDLoop & SourceSink$SeverityClass == "High"] <-
SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == a.high & SourceSink$SeverityClass == "High"]*ifelse(unique(SourceSink$Phase[SourceSink$FluxID == FluxIDLoop]) == "Flaming",global.vars$FlamingNMOG/global.vars$FlamingCO,global.vars$SmoulderingNMOG/global.vars$SmoulderingCO)
}

### the foliage, other, and fine root pools have retention terms that are simple 1- all the other fluxes, so have to be computed at the end:

  #FluxID: 4
#Source: SW Foliage
#sink: SW Foliage
#PLS: Green fraction of canopy remaining intact after fire
#Pseudocode: remainder of (consumed+litterfall)
#Notes: have to use logical statement here, google sheets version said 1-Mortality, but can be <0 unless logic is enforced here
#note2: given definition of CFB, this includes all foliage in merch and submerch

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 4 & SourceSink$SeverityClass == "Low"] <- 1-sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == "Softwood Foliage" & SourceSink$SeverityClass == "Low"],na.rm=TRUE)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 4 & SourceSink$SeverityClass == "Mod"] <- 1-sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == "Softwood Foliage" & SourceSink$SeverityClass == "Mod"],na.rm=TRUE)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 4 & SourceSink$SeverityClass == "High"] <- 1-sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == "Softwood Foliage" & SourceSink$SeverityClass == "High"],na.rm=TRUE)


#SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 4 & SourceSink$SeverityClass == "Low"] <- 1 - ( SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 5 & SourceSink$SeverityClass == "Low"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 6 & SourceSink$SeverityClass == "Low"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 7 & SourceSink$SeverityClass == "Low"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 8 & SourceSink$SeverityClass == "Low"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 101 & SourceSink$SeverityClass == "Low"])

#SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 4 & SourceSink$SeverityClass == "Mod"] <- 1 - ( SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 5 & SourceSink$SeverityClass == "Mod"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 6 & SourceSink$SeverityClass == "Mod"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 7 & SourceSink$SeverityClass == "Mod"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 8 & SourceSink$SeverityClass == "Mod"]+ SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 101 & SourceSink$SeverityClass == "Mod"])

#SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 4 & SourceSink$SeverityClass == "High"] <- 1 - ( SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 5 & SourceSink$SeverityClass == "High"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 6 & SourceSink$SeverityClass == "High"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 7 & SourceSink$SeverityClass == "High"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 8 & SourceSink$SeverityClass == "High"]+ SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 101 & SourceSink$SeverityClass == "High"])
 


#FluxID: 9
#Source: SW Other
#sink: SW Other
#PLS: surviving Live branches, stumps, small trees and bark
#Pseudocode: = 1-(consumption + killed of other pool)

#notes: tried this more complex equation previously, without effect.
#(1-(mortality rate of conifers)*branch fraction of "other" pool)+(1-(medium DOM consumption rate)*stump fraction of other pool)+(1-(mortality of small tree conifers in severity class)*small tree fraction of other pool)+(1-CFB*bark fraction of other pool)
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 9 & SourceSink$SeverityClass == "Low"] <- 1-sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == "Softwood Other" & SourceSink$SeverityClass == "Low"],na.rm=TRUE)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 9 & SourceSink$SeverityClass == "Mod"] <- 1-sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == "Softwood Other" & SourceSink$SeverityClass == "Mod"],na.rm=TRUE)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 9 & SourceSink$SeverityClass == "High"] <- 1-sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == "Softwood Other" & SourceSink$SeverityClass == "High"],na.rm=TRUE)

#SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 9 & SourceSink$SeverityClass == "Low"] <- 1 - (sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 10 & SourceSink$FluxID <= 13 & SourceSink$SeverityClass == "Low"]) + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 102 & SourceSink$SeverityClass == "Low"])

#SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 9 & SourceSink$SeverityClass == "Mod"] <- 1 - (sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 10 & SourceSink$FluxID <= 13 & SourceSink$SeverityClass == "Mod"]) + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 102 & SourceSink$SeverityClass == "Mod"])

#SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 9 & SourceSink$SeverityClass == "High"] <- 1 - (sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 10 & SourceSink$FluxID <= 13 & SourceSink$SeverityClass == "High"])  + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 102 & SourceSink$SeverityClass == "High"])


#FluxID: 22
#Source: SW fine roots
#sink: SW fine roots
#PLS: Surviving fine roots
#Pseudocode:  =1-(combustion rate of fine roots+mortality rate of fine roots)
#notes: computed at end of fine roots calculations, even though listed as Flux 22
# NOTE: debug needed on high severity, giving value of -0.002, so rounding problem??

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 22 & SourceSink$SeverityClass == "Low"] <- 1-sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == "Softwood Fine Roots" & SourceSink$SeverityClass == "Low"],na.rm=TRUE)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 22 & SourceSink$SeverityClass == "Mod"] <- 1-sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == "Softwood Fine Roots" & SourceSink$SeverityClass == "Mod"],na.rm=TRUE)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 22 & SourceSink$SeverityClass == "High"] <- 1-sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == "Softwood Fine Roots" & SourceSink$SeverityClass == "High"],na.rm=TRUE)


#SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 22 & SourceSink$SeverityClass == "Low"] <- 1 - (sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 23 & SourceSink$FluxID <= 27 & SourceSink$SeverityClass == "Low"])  + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 104 & SourceSink$SeverityClass == "Low"])

#SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 22 & SourceSink$SeverityClass == "Mod"] <- 1 - (sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 23 & SourceSink$FluxID <= 27 & SourceSink$SeverityClass == "Mod"])  + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 104 & SourceSink$SeverityClass == "Mod"])

#SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 22 & SourceSink$SeverityClass == "High"] <- 1 - (sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 23 & SourceSink$FluxID <= 27 & SourceSink$SeverityClass == "High"])  + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 104 & SourceSink$SeverityClass == "High"]) 



#FluxID: 31
#Source: HW Foliage
#sink: HW Foliage
#PLS: Green fraction of canopy remaining intact after fire
#Pseudocode: Remainder of fluxes 32:35 above
#note2: given definition of CFB, this includes all foliage in merch and submerch

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 31 & SourceSink$SeverityClass == "Low"] <- 1-sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == "Hardwood Foliage" & SourceSink$SeverityClass == "Low"],na.rm=TRUE)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 31 & SourceSink$SeverityClass == "Mod"] <- 1-sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == "Hardwood Foliage" & SourceSink$SeverityClass == "Mod"],na.rm=TRUE)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 31 & SourceSink$SeverityClass == "High"] <- 1-sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == "Hardwood Foliage" & SourceSink$SeverityClass == "High"],na.rm=TRUE)




#SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 31 & SourceSink$SeverityClass == 'Low'] <- 1 - ( SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 32 & SourceSink$SeverityClass == "Low"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 33 & SourceSink$SeverityClass == "Low"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 34 & SourceSink$SeverityClass == "Low"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 35 & SourceSink$SeverityClass == "Low"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 105 & SourceSink$SeverityClass == "Low"])

#SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 31 & SourceSink$SeverityClass == 'Mod'] <- 1 - ( SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 32 & SourceSink$SeverityClass == "Mod"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 33 & SourceSink$SeverityClass == "Mod"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 34 & SourceSink$SeverityClass == "Mod"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 35 & SourceSink$SeverityClass == "Mod"]+ SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 105 & SourceSink$SeverityClass == "Mod"])

#SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 31 & SourceSink$SeverityClass == 'High'] <- 1 - ( SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 32 & SourceSink$SeverityClass == "High"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 33 & SourceSink$SeverityClass == "High"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 34 & SourceSink$SeverityClass == "High"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 35 & SourceSink$SeverityClass == "High"] + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 105 & SourceSink$SeverityClass == "High"])



#FluxID: 36
#Source: HW Other
#sink: HW Other
#PLS: surviving Live branches, stumps, small trees and bark
#Pseudocode: = 1-(consumption + killed of other pool)

#notes: tried this more complex equation previously, without effect.
#(1-(mortality rate of conifers)*branch fraction of 'other' pool)+(1-(medium DOM consumption rate)*stump fraction of other pool)+(1-(mortality of small tree conifers in severity class)*small tree fraction of other pool)+(1-CFB*bark fraction of other pool)
#Notes: 

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 36 & SourceSink$SeverityClass == "Low"] <- 1-sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == "Hardwood Other" & SourceSink$SeverityClass == "Low"],na.rm=TRUE)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 36 & SourceSink$SeverityClass == "Mod"] <- 1-sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == "Hardwood Other" & SourceSink$SeverityClass == "Mod"],na.rm=TRUE)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 36 & SourceSink$SeverityClass == "High"] <- 1-sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == "Hardwood Other" & SourceSink$SeverityClass == "High"],na.rm=TRUE)



#SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 36 & SourceSink$SeverityClass == 'Low'] <- 1 - (sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 37 & SourceSink$FluxID <= 40 & SourceSink$SeverityClass == 'Low']) + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 106 & SourceSink$SeverityClass == "Low"])

#SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 36 & SourceSink$SeverityClass == 'Mod'] <- 1 - (sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 37 & SourceSink$FluxID <= 40 & SourceSink$SeverityClass == 'Mod'])+ SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 106 & SourceSink$SeverityClass == "Mod"])

#SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 36 & SourceSink$SeverityClass == 'High'] <- 1 - (sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 37 & SourceSink$FluxID <= 40 & SourceSink$SeverityClass == 'High']) + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 106 & SourceSink$SeverityClass == "High"])


#FluxID: 49
#Source: HW fine roots
#sink: HW fine roots
#PLS: Surviving fine roots
#Pseudocode:  =1-(combustion rate of fine roots+mortality rate of fine roots)
#notes: computed at end of fine roots calculations, even though listed as Flux 22

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 49 & SourceSink$SeverityClass == "Low"] <- 1-sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == "Hardwood Fine Roots" & SourceSink$SeverityClass == "Low"],na.rm=TRUE)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 49 & SourceSink$SeverityClass == "Mod"] <- 1-sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == "Hardwood Fine Roots" & SourceSink$SeverityClass == "Mod"],na.rm=TRUE)

SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 49 & SourceSink$SeverityClass == "High"] <- 1-sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == "Hardwood Fine Roots" & SourceSink$SeverityClass == "High"],na.rm=TRUE)



#SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 49 & SourceSink$SeverityClass == 'Low'] <- 1 - (sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 50 & SourceSink$FluxID <= 54 & SourceSink$SeverityClass == 'Low']) + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 108 & SourceSink$SeverityClass == "Low"])

#SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 49 & SourceSink$SeverityClass == 'Mod'] <- 1 - (sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 50 & SourceSink$FluxID <= 54 & SourceSink$SeverityClass == 'Mod']) + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 108 & SourceSink$SeverityClass == "Low"])

#SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 49 & SourceSink$SeverityClass == 'High'] <- 1 - (sum(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID >= 50 & SourceSink$FluxID <= 54 & SourceSink$SeverityClass == 'High']) + SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$FluxID == 108 & SourceSink$SeverityClass == "High"])


## end loop

  # final step in loop: once you have a list each built by ecozone, then build a higher-level list called "FireDM"
   
}

###convert SourceSink to a all-character array for export
  SourceSink.export <- apply(SourceSink,2,as.character)
  
##write to csv each time you build it.
write.csv(SourceSink.export,"FireDM-currents.csv")

```

```{r checkSum-not-run, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
##example calc:
#sum(SourceSink$Value[SourceSink$Ecozone == "BP" & SourceSink$Source == "Softwood Merchantable" & SourceSink$SeverityClass == "Mod"])

source.list.checksum <- c("Softwood Merchantable", "Softwood Foliage","Softwood Other","Softwood Submerchantable", "Softwood Coarse Roots","Softwood Fine Roots","Aboveground Very Fast DOM","Aboveground Fast DOM","Medium DOM","Aboveground Slow DOM","Softwood Stem Snag","Softwood Branch Snag","Hardwood Merchantable", "Hardwood Foliage","Hardwood Other","Hardwood Submerchantable","Hardwood Coarse roots","Hardwood Fine Roots","Hardwood Stem Snag","Hardwood Branch Snag","PM25","PM10","NMOG") 

#checksum for a single ecozone, single severity level:


##check the sinks:
for (i in seq(1:length(source.list.checksum))) {

  print(source.list.checksum[i])
  print(sum(SourceSink$Value[SourceSink$Ecozone == "BP" & SourceSink$Sink == source.list.checksum[i] & SourceSink$SeverityClass == "Mod"],na.rm=TRUE))
}

##check the source terms (no CO2 etc gas sources....):
for (i in seq(1:length(source.list.checksum))) {

  print(source.list.checksum[i])
  print(sum(SourceSink$Value[SourceSink$Ecozone == "BP" & SourceSink$Source == source.list.checksum[i] & SourceSink$SeverityClass == "Mod"],na.rm=TRUE))
}


```

```{r makeTables, echo=FALSE, message=FALSE, warning=FALSE}
 
## replace any NAs with blanks in kable tables
options(knitr.kable.NA = '')

  ### list for columns and rows in visual DM: can be any order, not linked to FluxID or anything:
### text here must exactly match the name of rows in SinkSource, however:

  sink.col.list <- c("Softwood Merchantable", "Softwood Stem Snag","Medium DOM","Softwood Foliage","Aboveground Very Fast DOM", "CO2", "CH4", "CO", "PM25")
  source.row.list <- c("Softwood Merchantable", "Softwood Stem Snag","Medium DOM","Softwood Foliage","Aboveground Very Fast DOM", "CO2", "CH4", "CO", "PM25")

  
  ###make this a function with attributes of ecozone and severity class:
  
  DMTables <- function(ecozone, SeverityClass) {
  
  DM.temp <- as.data.frame(array(NA,c(length(sink.col.list),length(sink.col.list))))
  
  for (j in seq(1:length(sink.col.list))) {
    for (k in seq(1:length(sink.col.list))) {
     
      #if the pair is blank, then return NA, otherwise, look through the list of sink/source pairs for the ecozone and severity level and return that value 
      ifelse(is.na(SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == source.row.list[j] & SourceSink$Sink == sink.col.list[k] & SourceSink$SeverityClass == SeverityClass]),NA,DM.temp[j,k] <- SourceSink$Value[SourceSink$Ecozone == ecozone & SourceSink$Source == source.row.list[j] & SourceSink$Sink == sink.col.list[k] & SourceSink$SeverityClass == SeverityClass])
     
      
    }
    
    
  } 
  rownames(DM.temp) <- source.row.list
  kbl(DM.temp[1:length(sink.col.list),1:length(sink.col.list)],col.names = c("Softwood Merchantable", "Softwood Stem Snag","Medium DOM
","Softwood Foliage","Aboveground Very Fast DOM", "CO2", "CH4", "CO", "PM25"), align = "c",caption = paste0(SeverityClass, " severity Disturbance Matrix in ", ecozone)) %>%
    kable_styling(full_width = F, html_font = "Cambria") %>%
column_spec(2:(length(sink.col.list) + 1), width = "2cm") %>%
column_spec(1, width = "3cm") %>%
  kableExtra::landscape() %>%
          kable_styling(latex_options = "scale_down")  %>%
  kable_styling(latex_options = "hold_position")
  
 
  
  }
  
 ##example of function, for BP and moderate severity (NOT RUN):
  ##DMTables(ecozone = "BP", SeverityClass = "Low") 
  ##DMTables(ecozone = "BP", SeverityClass = "Mod")
  DMTables(ecozone = "BP", SeverityClass = "High")
  
```

## Field case studies (for consideration)

```{r exp-fire-valid}

###table with rows are CBM pools, columns (paird) are obs and modelled exp fires

### fires that would work:

### ICFME (SW TP High); Sharpsands 2007 (SW BSE High), Lafoe (HW BSE Low), CWS C-7 burns (SW MC Mod), Carrot lake (SW MC High)

### variables specifically measured during an experimental fire, in the verbiage of the fire DMs:
exp.fire.table.defs <- c("SW.CFB","HW.CFB","SW.Mort","HW.Mort","SW.SubMerch.Mort","HW.SubMerch.Mort","SmTree.Mort","SW.Snag.Comb.Frac","HW.Snag.Comb.Frac","MedDOM.Comb.Frac", "Duff.consump.frac")

##then, take the list above, and look up the same row but the column "Plain.Language.Name" in FireDMTableDefs.csv:
## exp.fire.table.labels <-

##note that Duff.consump.frac is an ecozone variable, not in FireDMTableDefs.csv

##list of all possible CBM pools measured during an experimental fire:
exp.fire.pools <- c("Softwood Foliage","Softwood Other","Aboveground Very Fast DOM","Aboveground Fast DOM","Medium DOM","Aboveground Slow DOM","Softwood Stem Snag","Hardwood Other","Hardwood Stem Snag") 

###fun idea: ternary plots of live vs combusted vs dead for each of these fires, modelled vs observed?
##https://cran.r-project.org/web/packages/Ternary/vignettes/Ternary.html
## with the colour being the fuel type/leading spp and size being total emissions?
### can we draw lines in between pairs of mod vs obs in that package? TernaryApp function in the package should apparently let you draw connected points?
```

ICFME has detailed, for high severity.

Another option would be Lafoe Creek mixedwood burns, which would need some sort of CFB and mortality estimate. Is the pre-fire fuel load documented somewhere?

Pelican would work too, less on the bark consumption etc though.

And last, maybe something from Carrot lake or similarly well-observed BC fire?

Compare each pool's observed vs modelled relative consumption rates using (ideally) dNBR to drive severity class from the real data.

Use exactly the FBP DataFrame, no need for anything duplicating that otherwise. Am going to compute proportional combustion from the FBP Data frame anyways.

## 1990-2020(1) GCBM BC annual C stocks estimates with new fire DM scheme

Give quick summary here, show overview map of all the fires, and also an example of the GCBM biomass pools and also severity classes on a fire or two from Ellen

```{r BC-overview-map}

##maybe just a figure of the fires labelled by year and perhaps a pie(?) chart of their severity portions as mapped?

```

Then compare old vs new fire DM scheme for some (all?) individual fires as a biplot

```{r biplot}

### let's assume all the GCBM processing has been done.

### biplot of CO2e total per fire, comparing old scheme vs new.  Gets you an idea of how it scales vs size of fire.  Colour for ecozone within BC?

```

Then the annual GCBM runs with old and new scheme.

```{r time-series-BC-wildfires}

### let's assume all the GCBM processing has been done.

### times series or biplot?  Time series seems the one they default too. Maybe both?

### Just the two lines (old vs new) as CO2e per year, or do we get to also show anything else?  Maybe annual PM2.5 gets in an appendix, since there's no old vs new.

### fun followup graph: with the new system only (?) total area burned vs total CO2e, showing that there's not as much of a constant slope as you think?  That the CO2e/ha can really vary between years.

```

# Discussion

-some discussion points (unordered) so far

-   given the generic nature of these DMs and their simple relative simplicity, can be added to other frameworks like LANDIS (see Stenzel 2019 as well, they do some of that).

<!-- -->

-   paragraph on extended impacts like delayed stem mortality, rapid snag fall, and changes (or not) in duff decomposition rates. Not (as of yet) covered in this 1-timestep pulse disturbance described here.

# Conclusions

The conclusion goes here.

# Appendix A: list of fluxes and corresponding fire-related plain-language summary.

```{r SinkSourceGenericAppendix,  echo=FALSE, message=FALSE, warning=FALSE }

kbl(SourceSinkGeneric[SourceSinkGeneric$SeverityClass == 'Low',3:5],row.names = FALSE) %>%
    kable_styling(full_width = F, html_font = "Cambria") %>%
  kable_styling(latex_options = "scale_down")  %>%
  kable_styling(latex_options = "hold_position")
  
```

# Appendix B: annual variability in observed Drought Code during wildfire spread, and impact on ecozone-level DM calculations

```{r AnnualDC, echo=FALSE,message=FALSE, warning=FALSE}

###Load annual hotspot median DC by ecozone (via Quinn Barber and CFSDB)
DC.year <- read.csv("~/nrcan-cfs-fire/FireDMs/DC_by_ecozone_year.csv")
##which has the forest floor loading data from the FFFC dataframe already loaded in:

#apply de Groot's FFFC equation per year, using DC50
DC.year$Duff.consump.kg.m2 <- 0.016872*DC.year$DC50^0.71*DC.year$Median.Forest.Floor.Load.kg.m2^0.671 - Litter.Load

DC.year$Duff.consump.kg.m2 <- inv.logit(DC.year$DC50^0.33*DC.year$Median.Forest.Floor.Load.kg.m2^(-0.171)-4.8)*DC.year$Median.Forest.Floor.Load.kg.m2


##calculate fractional consumption
DC.year$Duff.consump.frac <- inv.logit(DC.year$DC50^0.33*DC.year$Median.Forest.Floor.Load.kg.m2^(-0.171)-4.8)



##if DC50 < 20, then set to DC=20
##not sure the source of DC50 == 0 in CFSDB....
DC.year$DC50 <- ifelse(DC.year$DC50<20,20,DC.year$DC50)


```

```{r AnnualDC-Vis-DC50, echo=FALSE,message=FALSE, warning=FALSE, fig.width=4,fig.height=3}
 
   ### the graphs, all time series: (1) annual DC by year; (2) absolute consumption values by year; (3) fractional consumption values by year; (4) will add in burned area by ecozone by year eventually too

ggplot(DC.year, aes(year,DC50,colour=Ecozone)) + geom_dl(aes(label = Ecozone, color = Ecozone), method=list("last.points",rot=30)) + geom_line() + ylab("Median Drought Code of fires in ecozone") +
  theme(legend.position="none")


```

```{r AnnualDC-Vis-Consump, echo=FALSE,message=FALSE, warning=FALSE, fig.width=4,fig.height=3}


ggplot(DC.year, aes(year,Duff.consump.kg.m2,colour=Ecozone)) + geom_dl(aes(label = Ecozone, color = Ecozone), method=list("last.points",rot=30)) + geom_line() + ylab("Modelled Duff Consumption, kg/m2") +
  theme(legend.position="none")
  

```

```{r AnnualDC-Vis-frac, echo=FALSE,message=FALSE, warning=FALSE, fig.width=4,fig.height=3}
 

ggplot(DC.year, aes(year,Duff.consump.frac,colour=Ecozone))+ geom_dl(aes(label = Ecozone, color = Ecozone), method=list("last.points",rot=30)) + geom_line() + ylab("Modelled duff consumption proportion") + theme(legend.position="none")

```

# Appendix C: DM template (can delete in final draft)

First, a generic template for a fire DM is loaded, that can represent any ecozone. It comes in two parts: (1) a list of variables, some biophysical and not relating to fire severity (such as the portion of live branchwood that falls into the smaller size fraction); or (2) severity-specific variables (such as Crown Fraction Burn) for a severity class. The template is loaded, and replicated across the list of ecozones (or any spatial unit) desired. Other processes, such as the analysis of field data, can then be used to fill in ecozone-specific variables in severity classes.

An example of the variable definition template is as follows:

```{r varDefsExample, echo=FALSE, message=FALSE, warning=FALSE}
kbl(head(VarDefs), caption = "Example of stored fire disturbance matrix precursor variable information") %>%
  kable_minimal()  %>%
          kable_styling(latex_options = "scale_down") %>%
  kable_styling(latex_options = "hold_position")



```

A plain language name for each variable is provided right in the data, as well.

A second template defines each flux in a Disturbance Matrix, with Source and Sink defined as precise character variables, and a plain language summary ("Process Synonym") included to tie this flux back to language used in the fire science literature. Pseudocode and notes are included in each flux, which is repeated for each fire severity class and ecozone. There are 3900 total fluxes, though many do not have sufficient information to describe differences between ecozones. Many of these are computed automatically, tying back into variables such as Crown Fraction Burned.

```{r SinkSourceExample, echo=FALSE, message=FALSE, warning=FALSE}
kbl(head(SourceSink), caption = "Sample of disturbance matrix data file") %>%
  kable_minimal() %>%
          kable_styling(latex_options = "scale_down") %>%
  kable_styling(latex_options = "hold_position") 



```

With both generic ecozone variables as well as severity-specific variables defined and the pseudocode for each flux included, actual DM values are computed as references to tables, subset by ecozone and severity class.

Note that rather than defining softwood crown fraction burned as a variable called "SW.CFB.Boreal.Plains" for each ecozone, there is a row in the VarDefs table that represents SW.CFB in each ecozone and for each severity class, thus avoiding the creation of large lists of manually entered variable names and values in the R environment. Instead, these values can be programmatically entered via external analysis of plot data (not covered here).

# Appendix D: Representative photos

Photos of: (1) partial litter consumption; (2) partial vs full duff consumption; (3) mortality but not consumption of understory trees with live overstory; (4) mortality but not consumption of overstory trees; (5) mixedwood severity example showing consumption of broadleaf foliage; (6) woody debris consumption; (7) snag preferential consumption relative to little to no bole consumption in live trees

Give lat/long, year, ecozone, severity class, and leading spp for each photo, maybe other relevant metrics? From some of the experimental fires mostly??

# Appendix E: List of Resprouting Hardwoods of Canada

Alnus spp. Arbutus men. Betula all. Betula pap. Betula pop. Fraxinus ame. Fraxinus nig. Fraxinus pen. Populus bal. Populus gra. Populus tre. Populus tri. Quercus spp. Salix spp.
